---
title: "Batch size optimization plotting"
author: "snd"
date: "12/11/2018"
output: html_document
---


# Batch size optimization plotting

```{r, include=FALSE}
library("devtools")
# install_github("sndean/packageSets")
library(packageSets)
packageSet(all)
```

```{r}
read_rocauc <- function(base_path, dataset_name){
  rocauc_out <- read_csv(paste(base_path, dataset_name, '/ROCAUC/ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
    bind_rows(., read_csv(paste(base_path, dataset_name, '/ROCAUC/ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>%
    bind_rows(., read_csv(paste(base_path, dataset_name, '/ROCAUC/ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
    na.omit() %>% 
    rename('dataset' = X1,
           'model' = X2,
           'micro' = X3,
           'macro' = X4)
  return(rocauc_out)
}
```







## Optimizing batch size for LSTM

LSTM_batchsize_optimization_121018

Constants: 
model = 0; 
LCN = 128, 128, 128, 128

Looped over 128 64 32 16 8 4 batch sizes


```{r, warning=FALSE, message=FALSE}
model_num <- 0
p <- '~/Desktop/LSTM_batchsize_optimization_121018/'
nums <- c(128, 64, 32, 16, 8, 4)

combined <- bind_rows(`Seawater (11 classes)` = read_rocauc(p, 'Seawater'), 
                      `Seawater (4 classes)` = read_rocauc(p, 'Seawater_4cats'), 
                      `Explosives (11 classes)` = read_rocauc(p, 'Explosives'), 
                      `Explosives (3 classes)` = read_rocauc(p, 'Explosives_3cats'), 
                      .id = 'dataset_label')

combined$lcn <- rep(nums, 12)
```



```{r, fig.height=9, fig.width=5}
combined %>% 
  filter(model == model_num) %>% 
  select(lcn, micro, macro, dataset_label) %>% 
  gather(k, v, -lcn, -dataset_label) %>% 
  mutate(
    lcn = factor(lcn, levels = rev(nums)),
    dataset_label = factor(dataset_label, levels = c('Seawater (4 classes)', 
                                                     'Seawater (11 classes)',
                                                     'Explosives (3 classes)',
                                                     'Explosives (11 classes)')),
    k = factor(k, levels = c('micro', 'macro'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 18) +
  geom_boxplot(aes(lcn, v, fill = dataset_label), color = 'black') +
  facet_grid(dataset_label~k, scales = 'free') +
  guides(fill=FALSE) +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(plot.title = element_text(size=12, color = "black", family="Arial")) +
  theme(strip.text.y = element_text(size=12, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  theme(strip.text.x = element_text(size=12, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  labs(x = 'Batch size', y = 'average AUC', title = 'LSTM, 500 epochs, batch size optimization')
```







## Optimizing batch size for FCN

FCN_batchsize_optimization_121018

Constants: 
model = 1; 
LCN = 0, 0, 0, 0

Looped over 128 64 32 16 8 4 batch sizes


```{r, warning=FALSE, message=FALSE}
model_num <- 1
p <- '~/Desktop/FCN_batchsize_optimization_121018/'
nums <- c(128, 64, 32, 16, 8, 4)

combined <- bind_rows(`Seawater (11 classes)` = read_rocauc(p, 'Seawater'), 
                      `Seawater (4 classes)` = read_rocauc(p, 'Seawater_4cats'), 
                      `Explosives (11 classes)` = read_rocauc(p, 'Explosives'), 
                      `Explosives (3 classes)` = read_rocauc(p, 'Explosives_3cats'), 
                      .id = 'dataset_label')

combined$lcn <- rep(nums, 12)
```



```{r, fig.height=9, fig.width=5}
combined %>% 
  filter(model == model_num) %>% 
  select(lcn, micro, macro, dataset_label) %>% 
  gather(k, v, -lcn, -dataset_label) %>% 
  mutate(
    lcn = factor(lcn, levels = rev(nums)),
    dataset_label = factor(dataset_label, levels = c('Seawater (4 classes)', 
                                                     'Seawater (11 classes)',
                                                     'Explosives (3 classes)',
                                                     'Explosives (11 classes)')),
    k = factor(k, levels = c('micro', 'macro'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 18) +
  geom_boxplot(aes(lcn, v, fill = dataset_label), color = 'black') +
  facet_grid(dataset_label~k, scales = 'free') +
  guides(fill=FALSE) +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(plot.title = element_text(size=12, color = "black", family="Arial")) +
  theme(strip.text.y = element_text(size=12, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  theme(strip.text.x = element_text(size=12, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  labs(x = 'Batch size', y = 'average AUC', title = 'FCN, 500 epochs, batch size optimization')
```














## Optimizing batch size for LSTM-FCN

LSTM_FCN_batchsize_optimization_121018

Constants: 
model = 2; 
LCN = 128, 64, 4, 8

Looped over 128 64 32 16 8 4 batch sizes


```{r, warning=FALSE, message=FALSE}
model_num <- 2
p <- '~/Desktop/LSTM_FCN_batchsize_optimization_121018/'
nums <- c(128, 64, 32, 16, 8, 4)

combined <- bind_rows(`Seawater (11 classes)` = read_rocauc(p, 'Seawater'), 
                      `Seawater (4 classes)` = read_rocauc(p, 'Seawater_4cats'), 
                      `Explosives (11 classes)` = read_rocauc(p, 'Explosives'), 
                      `Explosives (3 classes)` = read_rocauc(p, 'Explosives_3cats'), 
                      .id = 'dataset_label')

combined$lcn <- rep(nums, 12)
```



```{r, fig.height=9, fig.width=5}
combined %>% 
  filter(model == model_num) %>% 
  select(lcn, micro, macro, dataset_label) %>% 
  gather(k, v, -lcn, -dataset_label) %>% 
  mutate(
    lcn = factor(lcn, levels = rev(nums)),
    dataset_label = factor(dataset_label, levels = c('Seawater (4 classes)', 
                                                     'Seawater (11 classes)',
                                                     'Explosives (3 classes)',
                                                     'Explosives (11 classes)')),
    k = factor(k, levels = c('micro', 'macro'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 18) +
  geom_boxplot(aes(lcn, v, fill = dataset_label), color = 'black') +
  facet_grid(dataset_label~k, scales = 'free') +
  guides(fill=FALSE) +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(plot.title = element_text(size=12, color = "black", family="Arial")) +
  theme(strip.text.y = element_text(size=12, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  theme(strip.text.x = element_text(size=12, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  labs(x = 'Batch size', y = 'average AUC', title = 'LSTM-FCN, 500 epochs, batch size optimization')
```










## Optimizing batch size for ALSTM-FCN

ALSTM_FCN_batchsize_optimization_121018

Constants: 
model = 3; 
LCN = 128, 4, 4, 8

Looped over 128 64 32 16 8 4 batch sizes


```{r, warning=FALSE, message=FALSE}
model_num <- 3
p <- '~/Desktop/ALSTM_FCN_batchsize_optimization_121018/'
nums <- c(128, 64, 32, 16, 8, 4)

combined <- bind_rows(`Seawater (11 classes)` = read_rocauc(p, 'Seawater'), 
                      `Seawater (4 classes)` = read_rocauc(p, 'Seawater_4cats'), 
                      `Explosives (11 classes)` = read_rocauc(p, 'Explosives'), 
                      `Explosives (3 classes)` = read_rocauc(p, 'Explosives_3cats'), 
                      .id = 'dataset_label')

combined$lcn <- rep(nums, 12)
```

```{r, fig.height=9, fig.width=5}
combined %>% 
  filter(model == model_num) %>% 
  select(lcn, micro, macro, dataset_label) %>% 
  gather(k, v, -lcn, -dataset_label) %>% 
  mutate(
    lcn = factor(lcn, levels = rev(nums)),
    dataset_label = factor(dataset_label, levels = c('Seawater (4 classes)', 
                                                     'Seawater (11 classes)',
                                                     'Explosives (3 classes)',
                                                     'Explosives (11 classes)')),
    k = factor(k, levels = c('micro', 'macro'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 18) +
  geom_boxplot(aes(lcn, v, fill = dataset_label), color = 'black') +
  facet_grid(dataset_label~k, scales = 'free') +
  guides(fill=FALSE) +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(plot.title = element_text(size=12, color = "black", family="Arial")) +
  theme(strip.text.y = element_text(size=12, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  theme(strip.text.x = element_text(size=12, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  labs(x = 'Batch size', y = 'average AUC', title = 'ALSTM-FCN, 500 epochs, batch size optimization')
```


