---
title: "CAM and context vector plotting"
author: "snd"
date: "12/7/2018"
output: html_document
---


```{r, include=FALSE}
library("devtools")
# install_github("sndean/packageSets")
library(packageSets)
packageSet(all)
library(stringi)
```



# Check distribution

```{r}
read_csv('weights/Explosives_3cats_1_0_cam_1.csv') %>% 
  ggplot() +
  geom_histogram(aes(`0`), binwidth = 2)
```











# Plot time series

```{r}
read_csv('weights/Explosives_3cats_2_1_cam_1.csv') %>% 
  ggplot() +
  geom_line(aes(X1,`0`), size = 0.8) +
  theme_classic(base_size = 18) +
  # scale_y_reverse() +
  labs(x = 'Potential', y = 'Current') +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.text.x = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial"))
```



# Plot CAM

```{r}
read_csv('weights/Explosives_3cats_2_2_cam_2.csv') %>% 
  ggplot() +
  geom_line(aes(X1,`1`), size = 0.8) +
  theme_classic(base_size = 18) +
  # scale_y_reverse() +
  labs(x = 'Index', y = '') +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.text.x = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial"))
```
















# Faceting

`datasetprefix_model_class_cam_1or2`

If 3 classes: 0, 1, 2


```{r}
read_report <- function(filepath){
  report_out <- read_csv(filepath)
  return(report_out)
}

base_path <- 'cams/'
dataset <- 'Explosives_3cats/'

all_reports <- lapply(list.files(paste(base_path, dataset, sep = ''), full.names = TRUE), 
                      read_report)

names(all_reports) <- gsub(".txt",
                           "",
                           list.files(paste(base_path, dataset, sep = '')),
                           fixed = TRUE)

explosives_3cats <- bind_rows(all_reports, .id = 'file') %>% 
    filter(str_detect(file, '2.csv'))  ###### 1.csv or 2.csv
```


```{r}
explosives_3cats$file <- mapvalues(explosives_3cats$file, 
                                   from = unique(explosives_3cats$file), 
                                   to = c("A", "B", "C")
                                   )
```





```{r}
explosives_3cats %>%
  ggplot() +
  geom_line(aes(X1, `1`), size = 0.8) +  ####### `0` or `1`
  theme_classic(base_size = 18) +
  facet_grid(file~., scales = 'free') +
  labs(x = 'Index', y = '') +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.text.x = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(strip.text.y = element_text(size=16, color = "black", family="Arial"),
        strip.background = element_blank())
```




## Faceting over dataset classes and CAMs


### Explosives_3cats

```{r}
read_report <- function(filepath){
  report_out <- read_csv(filepath)
  return(report_out)
}

base_path <- 'cams/'
dataset <- 'Explosives_3cats/'

all_reports <- lapply(list.files(paste(base_path, dataset, sep = ''), full.names = TRUE), 
                      read_report)

names(all_reports) <- gsub(".txt",
                           "",
                           list.files(paste(base_path, dataset, sep = '')),
                           fixed = TRUE)

explosives_3cats_dataset <- bind_rows(all_reports, .id = 'file') %>% 
    filter(str_detect(file, '1.csv'))  ###### 1.csv or 2.csv

explosives_3cats_cams <- bind_rows(all_reports, .id = 'file') %>% 
    filter(str_detect(file, '2.csv'))  ###### 1.csv or 2.csv

explosives_3cats <- bind_cols(explosives_3cats_dataset, explosives_3cats_cams)

explosives_3cats$file <- mapvalues(explosives_3cats$file, 
                                   from = unique(explosives_3cats$file), 
                                   to = c("A", "B", "C")
)


explosives_3cats %>% 
  select(file, X1, `11`, `0`) %>% 
  rename(Data = `0`,
         CAM = `11`) %>% 
  gather(k, v, -X1, -file) %>% 
  mutate(
    k = factor(k, levels=c('Data', 'CAM'))
  ) %>% 
  ggplot() +
  geom_line(aes(X1, v), size = 0.8) +
  theme_bw(base_size = 18) +
  facet_grid(k~file, scales = 'free') +
  labs(x = 'Index', y = '', title = '                                           Class') +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.text.x = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(plot.title = element_text(size=16, color = "black", family="Arial")) +
  theme(strip.text.y = element_text(size=16, color = "black", family="Arial"),
        strip.background = element_blank())
  
```






### Seawater

```{r, fig.width=3, fig.height=12}
read_report <- function(filepath){
  report_out <- read_csv(filepath)
  return(report_out)
}

base_path <- 'cams/'
dataset <- 'Seawater/'

all_reports <- lapply(list.files(paste(base_path, dataset, sep = ''), full.names = TRUE), 
                      read_report)

names(all_reports) <- gsub(".txt",
                           "",
                           list.files(paste(base_path, dataset, sep = '')),
                           fixed = TRUE)

explosives_3cats_dataset <- bind_rows(all_reports, .id = 'file') %>% 
    filter(str_detect(file, '1.csv'))  ###### 1.csv or 2.csv

explosives_3cats_cams <- bind_rows(all_reports, .id = 'file') %>% 
    filter(str_detect(file, '2.csv'))  ###### 1.csv or 2.csv

explosives_3cats <- bind_cols(explosives_3cats_dataset, explosives_3cats_cams)

explosives_3cats$file <- mapvalues(explosives_3cats$file, 
                                   from = unique(explosives_3cats$file), 
                                   to = c("A", "B", "C", "D", "E", "F", "G", "H",
                                          "I", "J", "K")
)


explosives_3cats %>% 
  select(file, X1, `11`, `0`) %>% 
  rename(Data = `0`,
         CAM = `11`) %>% 
  gather(k, v, -X1, -file) %>% 
  mutate(
    k = factor(k, levels=c('Data', 'CAM'))
  ) %>% 
  filter(k == 'Data') %>% 
  # filter(k == 'CAM') %>%
  ggplot() +
  geom_line(aes(X1, v), size = 0.8) +
  theme_bw(base_size = 18) +
  facet_grid(rows = vars(file)) +
  # scale_y_continuous(limits = c(-2.5, 1)) + 
  labs(x = 'Index', y = '', title = '                                           Class') +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.text.x = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(plot.title = element_text(size=16, color = "black", family="Arial")) +
  theme(strip.text.y = element_text(size=16, color = "black", family="Arial"),
        strip.background = element_blank())
  
```











# Start from here (031219)

## Heatmap overlap with the dataset

Using gurbani2018 as an example

probably use grid.arrange to make the heatmap scale separate for each

make sure manual labeling is correct


### EXP-3

    python preprocessor.py -d ../unedited_data/Explosives_3cats.csv -p Explosives_3cats -c 0.3
    python trainer.py -d 11 -m 3 -r 1 -p Explosives_3cats -e 500

```{r}
# classes <- read_delim('../data/Explosives_3cats_labels.txt', delim=",", col_names = FALSE) %>% 
#   str_replace("'", "") %>% 
#   str_replace(" ", "") %>% 
#   str_replace("'", "") %>% 
#   stri_replace_all_fixed("[", "") %>% 
#   stri_replace_all_fixed("]", "")
```

```{r, fig.height=8, fig.width=6}
read_report <- function(filepath){
  report_out <- read_csv(filepath)
  return(report_out)
}

base_path <- 'cams/'
dataset <- 'Explosives_3cats/'
classes <- c('A', 'B', 'C')


all_reports <- lapply(list.files(paste(base_path, dataset, sep = ''), full.names = TRUE), 
                      read_report)

names(all_reports) <- gsub(".txt",
                           "",
                           list.files(paste(base_path, dataset, sep = '')),
                           fixed = TRUE)

explosives_3cats_dataset <- bind_rows(all_reports, .id = 'file') %>% 
    filter(str_detect(file, '1.csv'))  ###### 1.csv or 2.csv

explosives_3cats_cams <- bind_rows(all_reports, .id = 'file') %>% 
    filter(str_detect(file, '2.csv'))  ###### 1.csv or 2.csv

explosives_3cats <- bind_cols(explosives_3cats_dataset, explosives_3cats_cams)

explosives_3cats$file <- mapvalues(explosives_3cats$file, 
                                   from = unique(explosives_3cats$file), 
                                   to = classes
)




plist <- lapply(classes, function(i) 
  explosives_3cats %>% 
  select(file, X1, `11`, `0`) %>% 
  rename(Data = `0`,
         CAM = `11`) %>%
  filter(file == i) %>% 
  mutate(
    CAM = (CAM-min(CAM))/(max(CAM)-min(CAM))
  ) %>% 
  ggplot() +
  geom_bar(aes(x=X1, y=-50, fill=CAM), stat="identity", width=1.5) +
  geom_bar(aes(x=X1, y=50, fill=CAM), stat="identity", width=1.5) +
  geom_line(aes(X1, Data), size = 1.2) + 
  scale_fill_distiller(palette = "Spectral") +
  theme_classic(base_size = 18) +
  labs(x = 'Index', y = '', title = i) +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.text.x = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(plot.title = element_text(size=16, color = "black", family="Arial")) +
  theme(strip.text.y = element_text(size=16, color = "black", family="Arial"),
        strip.background = element_blank())
)

g <- grid.arrange(plist[[1]], plist[[2]], plist[[3]], 
             nrow = 3, ncol = 1)

ggsave(file="EXP3.tiff", g, dpi = 600)
```










### SW-11

    python preprocessor.py -d ../unedited_data/Seawater.csv -p Seawater -c 0.3
    python trainer.py -d 8 -m 2 -r 1 -p Seawater -e 1000

```{r}
# classes <- read_delim('../data/Seawater_labels.txt', delim=",", col_names = FALSE) %>% 
#   str_replace("'", "") %>% 
#   str_replace(" ", "") %>% 
#   str_replace("'", "") %>% 
#   stri_replace_all_fixed("[", "") %>% 
#   stri_replace_all_fixed("]", "")
```


```{r, fig.width=6, fig.height=27.5}
# ```{r, fig.width=16, fig.height=10}
# 

read_report <- function(filepath){
  report_out <- read_csv(filepath)
  return(report_out)
}

base_path <- 'cams/'
dataset <- 'Seawater/'
classes <- c('1', '2', '3', '4', '5', '6', '7', '8', '9', '10', '11')
classes <- c('BPA', 'MeP', 'Cd', 'Pb', 'Cu', 'DQ', 'HMM', 'Hg', 'Seawater', 'NP', 'PQ')

all_reports <- lapply(list.files(paste(base_path, dataset, sep = ''), full.names = TRUE), 
                      read_report)

names(all_reports) <- gsub(".txt",
                           "",
                           list.files(paste(base_path, dataset, sep = '')),
                           fixed = TRUE)

explosives_3cats_dataset <- bind_rows(all_reports, .id = 'file') %>% 
    filter(str_detect(file, '1.csv'))  ###### 1.csv or 2.csv

explosives_3cats_cams <- bind_rows(all_reports, .id = 'file') %>% 
    filter(str_detect(file, '2.csv'))  ###### 1.csv or 2.csv

explosives_3cats <- bind_cols(explosives_3cats_dataset, explosives_3cats_cams)

explosives_3cats$file <- mapvalues(explosives_3cats$file, 
                                   from = unique(explosives_3cats$file), 
                                   to = classes
)

plist <- lapply(classes, function(i) 
  explosives_3cats %>% 
  select(file, X1, `11`, `0`) %>% 
  rename(Data = `0`,
         CAM = `11`) %>%
  filter(file == i) %>% 
  mutate(
    CAM = (CAM-min(CAM))/(max(CAM)-min(CAM))
  ) %>% 
  ggplot() +
  geom_bar(aes(x=X1, y=-60, fill=CAM), stat="identity", width=1.5) +
  geom_bar(aes(x=X1, y=25, fill=CAM), stat="identity", width=1.5) +
  geom_line(aes(X1, Data), size = 1.2) + 
  scale_fill_distiller(palette = "Spectral") +
  theme_classic(base_size = 18) +
  labs(x = 'Index', y = '', title = i) +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.text.x = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(plot.title = element_text(size=16, color = "black", family="Arial")) +
  theme(strip.text.y = element_text(size=16, color = "black", family="Arial"),
        strip.background = element_blank())
)

g <- grid.arrange(plist[[1]], plist[[2]], plist[[3]], 
             plist[[4]], plist[[5]], plist[[6]],
             plist[[7]], plist[[8]], plist[[9]],
             plist[[10]], plist[[11]], nrow = 11, ncol = 1) # 11 x 1 or 3 x 4

ggsave(file="SW11.tiff", g, dpi = 600)
```










### SW-4

    python preprocessor.py -d ../unedited_data/Seawater_4cats.csv -p Seawater_4cats -c 0.3
    python trainer.py -d 9 -m 3 -r 1 -p Seawater_4cats -e 1000


```{r}
# classes <- read_delim('../data/Seawater_4cats_labels.txt', delim=",", col_names = FALSE) %>% 
#   str_replace("'", "") %>% 
#   str_replace(" ", "") %>% 
#   str_replace("'", "") %>% 
#   stri_replace_all_fixed("[", "") %>% 
#   stri_replace_all_fixed("]", "")
```

```{r, fig.height=10, fig.width=6}
read_report <- function(filepath){
  report_out <- read_csv(filepath)
  return(report_out)
}

base_path <- 'cams/'
dataset <- 'Seawater_4cats/'
classes <- c('HM', 'HandP', 'Ind', 'SW')

all_reports <- lapply(list.files(paste(base_path, dataset, sep = ''), full.names = TRUE), 
                      read_report)

names(all_reports) <- gsub(".txt",
                           "",
                           list.files(paste(base_path, dataset, sep = '')),
                           fixed = TRUE)

explosives_3cats_dataset <- bind_rows(all_reports, .id = 'file') %>% 
    filter(str_detect(file, '1.csv'))  ###### 1.csv or 2.csv

explosives_3cats_cams <- bind_rows(all_reports, .id = 'file') %>% 
    filter(str_detect(file, '2.csv'))  ###### 1.csv or 2.csv

explosives_3cats <- bind_cols(explosives_3cats_dataset, explosives_3cats_cams)

explosives_3cats$file <- mapvalues(explosives_3cats$file, 
                                   from = unique(explosives_3cats$file), 
                                   to = classes
)


plist <- lapply(classes, function(i) 
  explosives_3cats %>% 
  select(file, X1, `11`, `0`) %>% 
  rename(Data = `0`,
         CAM = `11`) %>%
  filter(file == i) %>% 
  mutate(
    CAM = (CAM-min(CAM))/(max(CAM)-min(CAM))
  ) %>% 
  ggplot() +
  geom_bar(aes(x=X1, y=-35, fill=CAM), stat="identity", width=1.5) +
  geom_bar(aes(x=X1, y=15, fill=CAM), stat="identity", width=1.5) +
  geom_line(aes(X1, Data), size = 1.2) + 
  scale_fill_distiller(palette = "Spectral") +
  theme_classic(base_size = 18) +
  labs(x = 'Index', y = '', title = i) +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.text.x = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(plot.title = element_text(size=16, color = "black", family="Arial")) +
  theme(strip.text.y = element_text(size=16, color = "black", family="Arial"),
        strip.background = element_blank())
)

g <- grid.arrange(plist[[1]], plist[[2]], plist[[3]], 
             plist[[4]], nrow = 4, ncol = 1)

ggsave(file="SW4.tiff", g, dpi = 600)
```





### EXP-11

    python preprocessor.py -d ../unedited_data/Explosives.csv -p Explosives -c 0.5
    python trainer.py -d 10 -m 2 -r 1 -p Explosives -e 1000
    
```{r}
# classes <- read_delim('../data/Explosives_labels.txt', delim="' ,", col_names = FALSE) %>% 
#   str_replace("'", "") %>% 
#   str_replace(" ", "") %>% 
#   str_replace("'", "") %>% 
#   stri_replace_all_fixed("[", "") %>% 
#   stri_replace_all_fixed("]", "")
# 
# classes
# 
# remove <- c(",", "")
# 
# classes <- classes[!classes %in% remove]
# 
# classes

```

```{r, fig.width=6, fig.height=27.5}
read_report <- function(filepath){
  report_out <- read_csv(filepath)
  return(report_out)
}

base_path <- 'cams/'
dataset <- 'Explosives/'
classes <- c("2,6 DNT", "1,3 DNB", "RDX", "1,3,5 TNB", "Tetryl", "TNT",
             "2am 4,6 DNT", "4am 2,6 DNT", "3NT", "2,4 DNT", "buffer")

all_reports <- lapply(list.files(paste(base_path, dataset, sep = ''), full.names = TRUE), 
                      read_report)

names(all_reports) <- gsub(".txt",
                           "",
                           list.files(paste(base_path, dataset, sep = '')),
                           fixed = TRUE)

explosives_3cats_dataset <- bind_rows(all_reports, .id = 'file') %>% 
    filter(str_detect(file, '1.csv'))  ###### 1.csv or 2.csv

explosives_3cats_cams <- bind_rows(all_reports, .id = 'file') %>% 
    filter(str_detect(file, '2.csv'))  ###### 1.csv or 2.csv

explosives_3cats <- bind_cols(explosives_3cats_dataset, explosives_3cats_cams)

explosives_3cats$file <- mapvalues(explosives_3cats$file,
                                   from = unique(explosives_3cats$file),
                                   to = classes
)

plist <- lapply(classes, function(i) 
  explosives_3cats %>% 
  select(file, X1, `11`, `0`) %>% 
  rename(Data = `0`,
         CAM = `11`) %>%
  filter(file == i) %>% 
  mutate(
    CAM = (CAM-min(CAM))/(max(CAM)-min(CAM))
  ) %>% 
  ggplot() +
  geom_bar(aes(x=X1, y=-65, fill=CAM), stat="identity", width=1.5) +
  geom_bar(aes(x=X1, y=60, fill=CAM), stat="identity", width=1.5) +
  geom_line(aes(X1, Data), size = 1.2) + 
  scale_fill_distiller(palette = "Spectral") +
  theme_classic(base_size = 18) +
  labs(x = 'Index', y = '', title = i) +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.text.x = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(plot.title = element_text(size=16, color = "black", family="Arial")) +
  theme(strip.text.y = element_text(size=16, color = "black", family="Arial"),
        strip.background = element_blank())
)

g <- grid.arrange(plist[[1]], plist[[2]], plist[[3]], 
             plist[[4]], plist[[5]], plist[[6]],
             plist[[7]], plist[[8]], plist[[9]],
             plist[[10]], plist[[11]], nrow = 11, ncol = 1)

ggsave(file="EXP11.tiff", g, dpi = 600)
```














#### Notes 

Can't use FCN until the generation of CAM for that model is fixed... so 1 --> 3

Remove previous cam files from directory before running


