---
title: "ROCAUC"
author: "snd"
date: "11/11/2018"
output: html_document
---


```{r}
library(tidyverse)
```




First run a bash script (e.g., `experiment.sh`) that results in certain files containing ROCAUC and other information being saved.






# 111418 ROCAUC boxplots


```{r}
path <- '~/results/epochs_500/Seawater/ROCAUC/'

rocauc1 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)

replacement_vec <- c("0"="LSTM", "1"="FCN", "2"="LSTM-FCN", "3"="ALSTM-FCN")
rocauc1$model <- str_replace_all(rocauc1$model, replacement_vec)
rocauc1
```

```{r}
path <- '~/results/epochs_500/Seawater_4cats/ROCAUC/'

rocauc2 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)

replacement_vec <- c("0"="LSTM", "1"="FCN", "2"="LSTM-FCN", "3"="ALSTM-FCN")
rocauc2$model <- str_replace_all(rocauc2$model, replacement_vec)
rocauc2
```


```{r}
combined <- bind_rows(Seawater_11=rocauc1, Seawater_4=rocauc2, .id = 'dataset_label')
combined$dataset_label <- str_replace_all(combined$dataset_label, "Seawater_11", "11 classes")
combined$dataset_label <- str_replace_all(combined$dataset_label, "Seawater_4", "4 classes")
```

```{r}
combined
```




```{r, fig.height=4, fig.width=6}
combined %>% 
  # select(model, micro, macro, dataset_label) %>% 
  select(model, micro, dataset_label) %>% 
  gather(k, v, -model, -dataset_label) %>% 
  mutate(
    model = factor(model, levels = c('LDA', 'LSTM', 'FCN', 'LSTM-FCN', 'ALSTM-FCN')),
    dataset_label = factor(dataset_label, levels = c('4 classes', '11 classes'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 18) +
  geom_boxplot(aes(model, v, fill = model)) + # , alpha = 0.4) +
  facet_grid(.~dataset_label, scales = 'free') +
  # facet_grid(dataset_label~k, scales = 'free') +
  guides(fill=FALSE) +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(strip.text.y = element_text(size=18, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  scale_y_continuous(limits = c(0.7, 1.0)) +
  labs(x = 'Model', y = 'micro-average AUC') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```









































# 111518 Batch size and LCN experiments

Batch size experiments can be performed on each LSTM, FCN, LSTM-FCN, and ALSTM-FCN.
LCN experiments can be performed on only LSTM, LSTM-FCN, and ALSTM-FCN.

The range for LCN appears to be limited to ≤128 because of index errors when attempting 256 cells. So it seems relatively symmetrical to go with the list of `128, 64, 32, 16, 8, 4` for both the batch size and LCN experiments. 

As of 11/15/18, it seems like:

 - the optimal batch size is 32
 - the optimal LCN for LSTM = 128, ALSTM-FCN = 64.
 
It's unclear whether altering the LCN for LSTM-FCN or ALSTM-FCN has much influence on the resulting performance of the model, whereas the trend for changing the LCN for the LSTM is clear: higher is better.






## Batch size experiment

          The dataset index 4 is for the dataset Seawater.
          Model number: 3. Where LSTM = 0, FCN = 1, LSTM-FCN = 2, ALSTM-FCN = $
          The model was run for 500 epochs with a batch size of 16.
          Run at 2018-11-12 17:01:52.


```{r}
path <- '~/results/batchsize_experiment_epochs_500/Seawater/ROCAUC/'  # path <- '~/results/Seawater_150epochs/ROCAUC/'

rocauc1 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)
rocauc1
```


```{r}
path <- '~/results/batchsize_experiment_epochs_500/Seawater_4cats/ROCAUC/'

rocauc2 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)

rocauc2
```


```{r}
combined <- bind_rows(Seawater_11=rocauc1, Seawater_4=rocauc2, .id = 'dataset_label')
combined$dataset_label <- str_replace_all(combined$dataset_label, "Seawater_11", "11 classes")
combined$dataset_label <- str_replace_all(combined$dataset_label, "Seawater_4", "4 classes")
```


```{r}
combined$batchsize <- rep(c(0, 128, 64, 32, 16), 6)
```



```{r, fig.height=6, fig.width=6}
combined %>% 
  filter(model == 3) %>% 
  select(batchsize, micro, macro, dataset_label) %>% 
  gather(k, v, -batchsize, -dataset_label) %>% 
  mutate(
    batchsize = factor(batchsize, levels = c(16, 32, 64, 128)),
    dataset_label = factor(dataset_label, levels = c('4 classes', '11 classes'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 18) +
  geom_boxplot(aes(batchsize, v), fill = 'lightgreen') +
  facet_grid(k~dataset_label, scales = 'free') +
  guides(fill=FALSE) +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(plot.title = element_text(size=12, color = "black", family="Arial")) +
  theme(strip.text.y = element_text(size=18, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  theme(strip.text.x = element_text(size=18, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  # scale_y_continuous(limits = c(0.85, 0.96)) +
  labs(x = 'batch size', y = 'average AUC', title = 'ALSTM-FCN, 500 epochs, Seawater')
```



```{r, fig.height=4, fig.width=6}
combined %>% 
  filter(model == 3) %>% 
  select(batchsize, micro, macro, dataset_label) %>% 
  gather(averaging, v, -batchsize, -dataset_label) %>% 
  mutate(
    batchsize = factor(batchsize, levels = c(16, 32, 64, 128)),
    dataset_label = factor(dataset_label, levels = c('4 classes', '11 classes')),
    averaging = factor(averaging, levels = c('micro', 'macro'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 18) +
  geom_boxplot(aes(batchsize, v, fill = averaging)) +
  facet_grid(.~dataset_label, scales = 'free') +
  # guides(fill=FALSE) +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(plot.title = element_text(size=12, color = "black", family="Arial")) +
  theme(strip.text.y = element_text(size=18, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  theme(strip.text.x = element_text(size=18, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  # scale_y_continuous(limits = c(0.85, 0.96)) +
  labs(x = 'batch size', y = 'average AUC', title = 'ALSTM-FCN, 500 epochs, Seawater')
```

























## LCN experiment

First test of LSTM cell number experiments, using ALSTM-FCN.

Output of `cat Seawater_3_parameters.txt`:

          The dataset index 4 is for the dataset Seawater.
          Model number: 3. Where LSTM = 0, FCN = 1, LSTM-FCN = 2, ALSTM-FCN = $
          The model was run for 500 epochs with a batch size of 32.
          Run at 2018-11-14 22:58:50.


32 16 8 4

```{r}
path <- '~/results/lcn_experiment_epochs_500/Seawater/ROCAUC/'  # path <- '~/results/Seawater_150epochs/ROCAUC/'

rocauc1 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)
rocauc1
```

```{r}
path <- '~/results/lcn_experiment_epochs_500/Seawater_4cats/ROCAUC/'

rocauc2 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)

rocauc2
```


```{r}
combined <- bind_rows(Seawater_11=rocauc1, Seawater_4=rocauc2, .id = 'dataset_label')
combined$dataset_label <- str_replace_all(combined$dataset_label, "Seawater_11", "11 classes")
combined$dataset_label <- str_replace_all(combined$dataset_label, "Seawater_4", "4 classes")
```


```{r}
combined$lcn <- rep(c(0, 32, 16, 8, 4), 3)
```


```{r}
combined
```


```{r, fig.height=6, fig.width=6}
combined %>% 
  filter(model == 3) %>% 
  select(lcn, micro, macro, dataset_label) %>% 
  gather(k, v, -lcn, -dataset_label) %>% 
  mutate(
    lcn = factor(lcn, levels = c(4, 8, 16, 32)),
    dataset_label = factor(dataset_label, levels = c('4 classes', '11 classes'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 18) +
  geom_boxplot(aes(lcn, v), fill = 'lightgreen') +
  # facet_grid(.~k, scales = 'free') +
  facet_grid(k~dataset_label, scales = 'free') +
  guides(fill=FALSE) +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(plot.title = element_text(size=12, color = "black", family="Arial")) +
  theme(strip.text.y = element_text(size=18, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  theme(strip.text.x = element_text(size=18, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  # scale_y_continuous(limits = c(0.85, 0.96)) +
  labs(x = 'LSTM cell number', y = 'average AUC', title = 'ALSTM-FCN, 500 epochs, Seawater')
```


Decided to run again with a larger range of numbers, next.
















### LSTM LCN optimization

Output of `cat Seawater_0_parameters.txt`:

          The dataset index 4 is for the dataset Seawater.
          Model number: 0. Where LSTM = 0, FCN = 1, LSTM-FCN = 2, ALSTM-FCN = $
          The model was run for 500 epochs with a batch size of 32.
          Run at 2018-11-15 10:16:28.


256, 128, 64, 32, 16, 8, 4

```{r}
path <- '~/results/LSTM_LCN_experiment/Seawater/ROCAUC/'  # path <- '~/results/Seawater_150epochs/ROCAUC/'

rocauc1 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)
rocauc1
```

```{r}
path <- '~/results/LSTM_LCN_experiment/Seawater_4cats/ROCAUC/'

rocauc2 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)

rocauc2
```


```{r}
combined <- bind_rows(Seawater_11=rocauc1, Seawater_4=rocauc2, .id = 'dataset_label')
combined$dataset_label <- str_replace_all(combined$dataset_label, "Seawater_11", "11 classes")
combined$dataset_label <- str_replace_all(combined$dataset_label, "Seawater_4", "4 classes")
```


```{r}
combined$lcn <- rep(c(0, 256, 128, 64, 32, 16, 8, 4), 6)
```


```{r}
combined %>% 
  filter(model == 0) %>% 
  select(lcn, micro, macro, dataset_label) %>% 
  gather(k, v, -lcn, -dataset_label) %>% 
  mutate(
    lcn = factor(lcn, levels = c(4, 8, 16, 32, 64, 128, 256)),
    dataset_label = factor(dataset_label, levels = c('4 classes', '11 classes'))
  ) 
```


```{r, fig.height=6, fig.width=6}
combined %>% 
  filter(model == 0) %>% 
  select(lcn, micro, macro, dataset_label) %>% 
  gather(k, v, -lcn, -dataset_label) %>% 
  mutate(
    lcn = factor(lcn, levels = c(4, 8, 16, 32, 64, 128, 256)),
    dataset_label = factor(dataset_label, levels = c('4 classes', '11 classes'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 18) +
  geom_boxplot(aes(lcn, v), fill = 'lightgreen') +
  # facet_grid(.~k, scales = 'free') +
  facet_grid(k~dataset_label, scales = 'free') +
  guides(fill=FALSE) +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(plot.title = element_text(size=12, color = "black", family="Arial")) +
  theme(strip.text.y = element_text(size=18, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  theme(strip.text.x = element_text(size=18, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(limits = c(0.25, 1)) +
  labs(x = 'LSTM cell number', y = 'average AUC', title = 'LSTM, 500 epochs, Seawater, LCN optimization')

  # ggsave('test.png')
```













### ALSTM-FCN LCN optimization

256, 128, 64, 32, 16, 8, 4 (256 failed because the index is too large)

Output from `cat nano Seawater_3_parameters.txt`:

          The dataset index 4 is for the dataset Seawater.
          Model number: 3. Where LSTM = 0, FCN = 1, LSTM-FCN = 2, ALSTM-FCN = $
          The model was run for 500 epochs with a batch size of 32.
          Run at 2018-11-15 15:32:26.

```{r}
path <- '~/results/ALSTMFCN_LCN_experiment/Seawater/ROCAUC/'  # path <- '~/results/Seawater_150epochs/ROCAUC/'

rocauc1 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)
rocauc1
```

```{r}
path <- '~/results/ALSTMFCN_LCN_experiment/Seawater_4cats/ROCAUC/'

rocauc2 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)

rocauc2
```


```{r}
combined <- bind_rows(Seawater_11=rocauc1, Seawater_4=rocauc2, .id = 'dataset_label')
combined$dataset_label <- str_replace_all(combined$dataset_label, "Seawater_11", "11 classes")
combined$dataset_label <- str_replace_all(combined$dataset_label, "Seawater_4", "4 classes")
```

```{r}
combined
```



```{r}
combined$lcn <- rep(c(0, 128, 64, 32, 16, 8, 4), 6)
```


```{r}
combined %>% 
  filter(model == 3) %>% 
  select(lcn, micro, macro, dataset_label) %>% 
  gather(k, v, -lcn, -dataset_label) %>% 
  mutate(
    lcn = factor(lcn, levels = c(4, 8, 16, 32, 64, 128, 256)),
    dataset_label = factor(dataset_label, levels = c('4 classes', '11 classes'))
  ) 
```


```{r, fig.height=6, fig.width=6}
combined %>% 
  filter(model == 3) %>% 
  select(lcn, micro, macro, dataset_label) %>% 
  gather(k, v, -lcn, -dataset_label) %>% 
  mutate(
    lcn = factor(lcn, levels = c(4, 8, 16, 32, 64, 128)),
    dataset_label = factor(dataset_label, levels = c('4 classes', '11 classes'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 18) +
  geom_boxplot(aes(lcn, v), fill = 'lightgreen') +
  # facet_grid(.~k, scales = 'free') +
  facet_grid(k~dataset_label, scales = 'free') +
  guides(fill=FALSE) +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(plot.title = element_text(size=12, color = "black", family="Arial")) +
  theme(strip.text.y = element_text(size=18, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  theme(strip.text.x = element_text(size=18, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  # scale_y_continuous(limits = c(0.25, 1)) +
  labs(x = 'LSTM cell number', y = 'average AUC', title = 'ALSTM-FCN, 500 epochs, Seawater, LCN optimization')

  # ggsave('test.png')
```






































# 111518 Plotting full ROCs (micro- and macro-average)


```{r}
path <- '~/results/rep_ROC_111518/'

LDA <- read_csv(paste(path, 'Seawater_LDA_micro_macro.csv', sep = ''))
LSTM <- read_csv(paste(path, 'Seawater_0_micro_macro.csv', sep = ''))
FCN <- read_csv(paste(path, 'Seawater_1_micro_macro.csv', sep = ''))
LSTM_FCN <- read_csv(paste(path, 'Seawater_2_micro_macro.csv', sep = ''))
ALSTM_FCN <- read_csv(paste(path, 'Seawater_3_micro_macro.csv', sep = ''))
combined <- bind_rows(LDA=LDA, 
                      LSTM=LSTM,
                      FCN=FCN,
                      `LSTM-FCN`=LSTM_FCN,
                      `ALSTM-FCN`=ALSTM_FCN,
                      .id = 'model')
```



```{r}
combined
```


```{r, fig.height=4, fig.width=6}
combined %>% 
  mutate(
    model = factor(model, levels = c('LDA', 'LSTM', 'FCN', 'LSTM-FCN', 'ALSTM-FCN'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 16) + 
  geom_line(aes(fpr_micro, tpr_micro, color = model), size = 1.5) +
  scale_x_continuous(limits = c(0, 1)) +
  scale_y_continuous(limits = c(0, 1)) +
  geom_abline(intercept = 0, slope = 1, color = 'black', linetype = 'dashed', size = 0.5) + 
  labs(x = 'False Positive Rate', y = 'True Positive Rate', color = '') +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial"))
```




```{r}
path <- '~/results/rep_ROC_111518/'

LDA <- read_csv(paste(path, 'Seawater_4cats_LDA_micro_macro.csv', sep = ''))
LSTM <- read_csv(paste(path, 'Seawater_4cats_0_micro_macro.csv', sep = ''))
FCN <- read_csv(paste(path, 'Seawater_4cats_1_micro_macro.csv', sep = ''))
LSTM_FCN <- read_csv(paste(path, 'Seawater_4cats_2_micro_macro.csv', sep = ''))
ALSTM_FCN <- read_csv(paste(path, 'Seawater_4cats_3_micro_macro.csv', sep = ''))
combined1 <- bind_rows(LDA=LDA, 
                      LSTM=LSTM,
                      FCN=FCN,
                      `LSTM-FCN`=LSTM_FCN,
                      `ALSTM-FCN`=ALSTM_FCN,
                      .id = 'model')
```

```{r, fig.height=4, fig.width=6}
combined1 %>% 
  mutate(
    model = factor(model, levels = c('LDA', 'LSTM', 'FCN', 'LSTM-FCN', 'ALSTM-FCN'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 16) + 
  geom_line(aes(fpr_micro, tpr_micro, color = model), size = 1.5) +
  scale_x_continuous(limits = c(0, 1)) +
  scale_y_continuous(limits = c(0, 1)) +
  geom_abline(intercept = 0, slope = 1, color = 'black', linetype = 'dashed', size = 0.5) + 
  labs(x = 'False Positive Rate', y = 'True Positive Rate', color = '') +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial"))
```





## Faceted micro

```{r}
combined2 <- bind_rows(`11 classes`=combined, 
                      `4 classes`=combined1,
                      .id = 'dataset_label')
```

```{r, fig.height=4, fig.width=8}
combined2 %>% 
  mutate(
    model = factor(model, levels = c('LDA', 'LSTM', 'FCN', 'LSTM-FCN', 'ALSTM-FCN')),
    dataset_label = factor(dataset_label, levels = c('4 classes', '11 classes'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 16) + 
  geom_line(aes(fpr_micro, tpr_micro, color = model), size = 1.5) +
  facet_grid(.~dataset_label, scales = 'free') +
  scale_x_continuous(limits = c(0, 1)) +
  scale_y_continuous(limits = c(0, 1)) +
  geom_abline(intercept = 0, slope = 1, color = 'black', linetype = 'dashed', size = 0.5) + 
  labs(x = 'False Positive Rate', y = 'True Positive Rate', color = '') +
  theme(axis.text = element_text(size=12, color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(strip.text.y = element_text(color = "black", family="Arial"), 
        strip.background = element_blank()) +
  theme(strip.text.x = element_text(color = "black", family="Arial"), 
        strip.background = element_blank())
```

## Faceted macro


```{r, fig.height=4, fig.width=8}
combined2 %>% 
  mutate(
    model = factor(model, levels = c('LDA', 'LSTM', 'FCN', 'LSTM-FCN', 'ALSTM-FCN')),
    dataset_label = factor(dataset_label, levels = c('4 classes', '11 classes'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 16) + 
  geom_line(aes(fpr_macro, tpr_macro, color = model), size = 1.5) +
  facet_grid(.~dataset_label, scales = 'free') +
  scale_x_continuous(limits = c(0, 1)) +
  scale_y_continuous(limits = c(0, 1)) +
  geom_abline(intercept = 0, slope = 1, color = 'black', linetype = 'dashed', size = 0.5) + 
  labs(x = 'False Positive Rate', y = 'True Positive Rate', color = '') +
  theme(axis.text = element_text(size=12, color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(strip.text.y = element_text(color = "black", family="Arial"), 
        strip.background = element_blank()) +
  theme(strip.text.x = element_text(color = "black", family="Arial"), 
        strip.background = element_blank())
```








# 111618 ROCAUC boxplots



```{r}
path <- '~/results/rocauc_boxplot_111618/Seawater/ROCAUC/'

rocauc1 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)

replacement_vec <- c("0"="LSTM", "1"="FCN", "2"="LSTM-FCN", "3"="ALSTM-FCN")
rocauc1$model <- str_replace_all(rocauc1$model, replacement_vec)
rocauc1
```

```{r}
path <- '~/results/rocauc_boxplot_111618/Seawater_4cats/ROCAUC/'

rocauc2 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)

replacement_vec <- c("0"="LSTM", "1"="FCN", "2"="LSTM-FCN", "3"="ALSTM-FCN")
rocauc2$model <- str_replace_all(rocauc2$model, replacement_vec)
rocauc2
```


```{r}
combined <- bind_rows(Seawater_11=rocauc1, Seawater_4=rocauc2, .id = 'dataset_label')
combined$dataset_label <- str_replace_all(combined$dataset_label, "Seawater_11", "11 classes")
combined$dataset_label <- str_replace_all(combined$dataset_label, "Seawater_4", "4 classes")
```

```{r}
combined
```


## Micro

```{r, fig.height=4, fig.width=6}
combined %>% 
  # select(model, micro, macro, dataset_label) %>% 
  select(model, micro, dataset_label) %>% 
  gather(k, v, -model, -dataset_label) %>% 
  mutate(
    model = factor(model, levels = c('LDA', 'LSTM', 'FCN', 'LSTM-FCN', 'ALSTM-FCN')),
    dataset_label = factor(dataset_label, levels = c('4 classes', '11 classes'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 18) +
  geom_boxplot(aes(model, v, fill = model)) +
  facet_grid(.~dataset_label, scales = 'free_y') +
  # facet_grid(dataset_label~k, scales = 'free') +
  guides(fill=FALSE) +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(strip.text.x = element_text(size=18, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  scale_y_continuous(limits = c(0.65, 1.0)) +
  labs(x = 'Model', y = 'micro-average AUC') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


## Macro

```{r, fig.height=4, fig.width=6}
combined %>% 
  # select(model, micro, macro, dataset_label) %>% 
  select(model, macro, dataset_label) %>% 
  gather(k, v, -model, -dataset_label) %>% 
  mutate(
    model = factor(model, levels = c('LDA', 'LSTM', 'FCN', 'LSTM-FCN', 'ALSTM-FCN')),
    dataset_label = factor(dataset_label, levels = c('4 classes', '11 classes'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 18) +
  geom_boxplot(aes(model, v, fill = model)) +
  facet_grid(.~dataset_label, scales = 'free_y') +
  # facet_grid(dataset_label~k, scales = 'free') +
  guides(fill=FALSE) +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(strip.text.x = element_text(size=18, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  scale_y_continuous(limits = c(0.65, 1.0)) +
  labs(x = 'Model', y = 'macro-average AUC') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

























# 111618 plotting ROC curves (micro- and macro-average)


```{r}
path <- '~/results/rocauc_boxplot_111618/Seawater/rep_ROC/'

LDA <- read_csv(paste(path, 'Seawater_LDA_micro_macro.csv', sep = ''))
LSTM <- read_csv(paste(path, 'Seawater_0_micro_macro.csv', sep = ''))
FCN <- read_csv(paste(path, 'Seawater_1_micro_macro.csv', sep = ''))
LSTM_FCN <- read_csv(paste(path, 'Seawater_2_micro_macro.csv', sep = ''))
ALSTM_FCN <- read_csv(paste(path, 'Seawater_3_micro_macro.csv', sep = ''))
combined <- bind_rows(LDA=LDA, 
                      LSTM=LSTM,
                      FCN=FCN,
                      `LSTM-FCN`=LSTM_FCN,
                      `ALSTM-FCN`=ALSTM_FCN,
                      .id = 'model')
```



```{r}
combined
```


```{r, fig.height=4, fig.width=6}
combined %>% 
  mutate(
    model = factor(model, levels = c('LDA', 'LSTM', 'FCN', 'LSTM-FCN', 'ALSTM-FCN'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 16) + 
  geom_line(aes(fpr_micro, tpr_micro, color = model), size = 1.5) +
  scale_x_continuous(limits = c(0, 1)) +
  scale_y_continuous(limits = c(0, 1)) +
  geom_abline(intercept = 0, slope = 1, color = 'black', linetype = 'dashed', size = 0.5) + 
  labs(x = 'False Positive Rate', y = 'True Positive Rate', color = '') +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial"))
```




```{r}
path <- '~/results/rocauc_boxplot_111618/Seawater_4cats/rep_ROC/'


LDA <- read_csv(paste(path, 'Seawater_4cats_LDA_micro_macro.csv', sep = ''))
LSTM <- read_csv(paste(path, 'Seawater_4cats_0_micro_macro.csv', sep = ''))
FCN <- read_csv(paste(path, 'Seawater_4cats_1_micro_macro.csv', sep = ''))
LSTM_FCN <- read_csv(paste(path, 'Seawater_4cats_2_micro_macro.csv', sep = ''))
ALSTM_FCN <- read_csv(paste(path, 'Seawater_4cats_3_micro_macro.csv', sep = ''))
combined1 <- bind_rows(LDA=LDA, 
                      LSTM=LSTM,
                      FCN=FCN,
                      `LSTM-FCN`=LSTM_FCN,
                      `ALSTM-FCN`=ALSTM_FCN,
                      .id = 'model')
```

```{r, fig.height=4, fig.width=6}
combined1 %>% 
  mutate(
    model = factor(model, levels = c('LDA', 'LSTM', 'FCN', 'LSTM-FCN', 'ALSTM-FCN'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 16) + 
  geom_line(aes(fpr_micro, tpr_micro, color = model), size = 1.5) +
  scale_x_continuous(limits = c(0, 1)) +
  scale_y_continuous(limits = c(0, 1)) +
  geom_abline(intercept = 0, slope = 1, color = 'black', linetype = 'dashed', size = 0.5) + 
  labs(x = 'False Positive Rate', y = 'True Positive Rate', color = '') +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial"))
```





## Faceted micro

```{r}
combined2 <- bind_rows(`11 classes`=combined, 
                      `4 classes`=combined1,
                      .id = 'dataset_label')
```

```{r, fig.height=4, fig.width=8}
combined2 %>% 
  mutate(
    model = factor(model, levels = c('LDA', 'LSTM', 'FCN', 'LSTM-FCN', 'ALSTM-FCN')),
    dataset_label = factor(dataset_label, levels = c('4 classes', '11 classes'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 18) + 
  geom_line(aes(fpr_micro, tpr_micro, color = model), size = 1.5) +
  facet_grid(.~dataset_label, scales = 'free') +
  scale_x_continuous(limits = c(0, 1)) +
  scale_y_continuous(limits = c(0, 1)) +
  geom_abline(intercept = 0, slope = 1, color = 'black', linetype = 'dashed', size = 0.5) + 
  labs(x = 'False Positive Rate', y = 'True Positive Rate', color = '') +
  theme(axis.text = element_text(size=12, color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(strip.text.x = element_text(size=18, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  theme(strip.text.x = element_text(color = "black", family="Arial"), 
        strip.background = element_blank())
```

## Faceted macro


```{r, fig.height=4, fig.width=8}
combined2 %>% 
  mutate(
    model = factor(model, levels = c('LDA', 'LSTM', 'FCN', 'LSTM-FCN', 'ALSTM-FCN')),
    dataset_label = factor(dataset_label, levels = c('4 classes', '11 classes'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 16) + 
  geom_line(aes(fpr_macro, tpr_macro, color = model), size = 1.5) +
  facet_grid(.~dataset_label, scales = 'free') +
  scale_x_continuous(limits = c(0, 1)) +
  scale_y_continuous(limits = c(0, 1)) +
  geom_abline(intercept = 0, slope = 1, color = 'black', linetype = 'dashed', size = 0.5) + 
  labs(x = 'False Positive Rate', y = 'True Positive Rate', color = '') +
  theme(axis.text = element_text(size=12, color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(strip.text.y = element_text(color = "black", family="Arial"), 
        strip.background = element_blank()) +
  theme(strip.text.x = element_text(color = "black", family="Arial"), 
        strip.background = element_blank())
```






# 111618 another LCN test (all at 128)

Seeing what happens if all LCNs are set to 128, like the well-(over?) performing LSTM. Everything else set the same as earlier today.

Earlier today: `array3=(128 0 64 64)`.

Now: `array3=(128 0 128 128)`


```{r}
path <- '~/results/LCN_experiment_all_128_111618/Seawater/ROCAUC/'

rocauc1 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)

replacement_vec <- c("0"="LSTM", "1"="FCN", "2"="LSTM-FCN", "3"="ALSTM-FCN")
rocauc1$model <- str_replace_all(rocauc1$model, replacement_vec)
rocauc1
```

```{r}
path <- '~/results/LCN_experiment_all_128_111618/Seawater_4cats/ROCAUC/'

rocauc2 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)

replacement_vec <- c("0"="LSTM", "1"="FCN", "2"="LSTM-FCN", "3"="ALSTM-FCN")
rocauc2$model <- str_replace_all(rocauc2$model, replacement_vec)
rocauc2
```


```{r}
combined <- bind_rows(Seawater_11=rocauc1, Seawater_4=rocauc2, .id = 'dataset_label')
combined$dataset_label <- str_replace_all(combined$dataset_label, "Seawater_11", "11 classes")
combined$dataset_label <- str_replace_all(combined$dataset_label, "Seawater_4", "4 classes")
```

```{r}
combined
```


## Micro

```{r, fig.height=4, fig.width=6}
combined %>% 
  # select(model, micro, macro, dataset_label) %>% 
  select(model, micro, dataset_label) %>% 
  gather(k, v, -model, -dataset_label) %>% 
  mutate(
    model = factor(model, levels = c('LDA', 'LSTM', 'FCN', 'LSTM-FCN', 'ALSTM-FCN')),
    dataset_label = factor(dataset_label, levels = c('4 classes', '11 classes'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 18) +
  geom_boxplot(aes(model, v, fill = model)) +
  facet_grid(.~dataset_label, scales = 'free_y') +
  # facet_grid(dataset_label~k, scales = 'free') +
  guides(fill=FALSE) +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(strip.text.x = element_text(size=18, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  scale_y_continuous(limits = c(0.6, 1.0)) +
  labs(x = 'Model', y = 'micro-average AUC') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


## Macro

```{r, fig.height=4, fig.width=6}
combined %>% 
  # select(model, micro, macro, dataset_label) %>% 
  select(model, macro, dataset_label) %>% 
  gather(k, v, -model, -dataset_label) %>% 
  mutate(
    model = factor(model, levels = c('LDA', 'LSTM', 'FCN', 'LSTM-FCN', 'ALSTM-FCN')),
    dataset_label = factor(dataset_label, levels = c('4 classes', '11 classes'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 18) +
  geom_boxplot(aes(model, v, fill = model)) +
  facet_grid(.~dataset_label, scales = 'free_y') +
  # facet_grid(dataset_label~k, scales = 'free') +
  guides(fill=FALSE) +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(strip.text.x = element_text(size=18, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  scale_y_continuous(limits = c(0.6, 1.0)) +
  labs(x = 'Model', y = 'macro-average AUC') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

Maybe easier to just go with 128 for each. It doesn't seem like 64 is significantly different (better or worse). 128 may even be better. 





































# SPACE

# NO GEN BELOW


# 111618 seeing what no_gen looks like

No gen
All batch sizes: 8
All LCNs: 8


```{r}
path <- '~/results/no_gen_all_lcn_128_bs_8_111618/Seawater/ROCAUC/'

rocauc1 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)

replacement_vec <- c("0"="LSTM", "1"="FCN", "2"="LSTM-FCN", "3"="ALSTM-FCN")
rocauc1$model <- str_replace_all(rocauc1$model, replacement_vec)
rocauc1
```

```{r}
path <- '~/results/no_gen_all_lcn_128_bs_8_111618/Seawater_4cats/ROCAUC/'

rocauc2 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)

replacement_vec <- c("0"="LSTM", "1"="FCN", "2"="LSTM-FCN", "3"="ALSTM-FCN")
rocauc2$model <- str_replace_all(rocauc2$model, replacement_vec)
rocauc2
```


```{r}
combined <- bind_rows(Seawater_11=rocauc1, Seawater_4=rocauc2, .id = 'dataset_label')
combined$dataset_label <- str_replace_all(combined$dataset_label, "Seawater_11", "11 classes")
combined$dataset_label <- str_replace_all(combined$dataset_label, "Seawater_4", "4 classes")
```

```{r}
combined
```


## Micro

```{r, fig.height=4, fig.width=6}
combined %>% 
  # select(model, micro, macro, dataset_label) %>% 
  select(model, micro, dataset_label) %>% 
  gather(k, v, -model, -dataset_label) %>% 
  mutate(
    model = factor(model, levels = c('LDA', 'LSTM', 'FCN', 'LSTM-FCN', 'ALSTM-FCN')),
    dataset_label = factor(dataset_label, levels = c('4 classes', '11 classes'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 18) +
  geom_boxplot(aes(model, v, fill = model)) +
  facet_grid(.~dataset_label, scales = 'free') +
  # facet_grid(dataset_label~k, scales = 'free') +
  guides(fill=FALSE) +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(strip.text.x = element_text(size=18, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  # scale_y_continuous(limits = c(0.85, 1.0)) +
  labs(x = 'Model', y = 'micro-average AUC') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


## Macro

```{r, fig.height=4, fig.width=6}
combined %>% 
  # select(model, micro, macro, dataset_label) %>% 
  select(model, macro, dataset_label) %>% 
  gather(k, v, -model, -dataset_label) %>% 
  mutate(
    model = factor(model, levels = c('LDA', 'LSTM', 'FCN', 'LSTM-FCN', 'ALSTM-FCN')),
    dataset_label = factor(dataset_label, levels = c('4 classes', '11 classes'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 18) +
  geom_boxplot(aes(model, v, fill = model)) +
  facet_grid(.~dataset_label, scales = 'free_y') +
  # facet_grid(dataset_label~k, scales = 'free') +
  guides(fill=FALSE) +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(strip.text.x = element_text(size=18, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  # scale_y_continuous(limits = c(0.6, 1.0)) +
  labs(x = 'Model', y = 'macro-average AUC') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```






# 111618 no_gen plotting ROC curves


```{r}
path <- '~/results/no_gen_all_lcn_128_bs_8_111618/Seawater/rep_ROC/'

LDA <- read_csv(paste(path, 'Seawater_LDA_micro_macro.csv', sep = ''))
LSTM <- read_csv(paste(path, 'Seawater_0_micro_macro.csv', sep = ''))
FCN <- read_csv(paste(path, 'Seawater_1_micro_macro.csv', sep = ''))
LSTM_FCN <- read_csv(paste(path, 'Seawater_2_micro_macro.csv', sep = ''))
ALSTM_FCN <- read_csv(paste(path, 'Seawater_3_micro_macro.csv', sep = ''))
combined <- bind_rows(LDA=LDA, 
                      LSTM=LSTM,
                      FCN=FCN,
                      `LSTM-FCN`=LSTM_FCN,
                      `ALSTM-FCN`=ALSTM_FCN,
                      .id = 'model')
```



```{r}
combined
```


```{r, fig.height=4, fig.width=6}
combined %>% 
  mutate(
    model = factor(model, levels = c('LDA', 'LSTM', 'FCN', 'LSTM-FCN', 'ALSTM-FCN'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 16) + 
  geom_line(aes(fpr_micro, tpr_micro, color = model), size = 1.5) +
  scale_x_continuous(limits = c(0, 1)) +
  scale_y_continuous(limits = c(0, 1)) +
  geom_abline(intercept = 0, slope = 1, color = 'black', linetype = 'dashed', size = 0.5) + 
  labs(x = 'False Positive Rate', y = 'True Positive Rate', color = '') +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial"))
```




```{r}
path <- '~/results/no_gen_all_lcn_128_bs_8_111618/Seawater_4cats/rep_ROC/'


LDA <- read_csv(paste(path, 'Seawater_4cats_LDA_micro_macro.csv', sep = ''))
LSTM <- read_csv(paste(path, 'Seawater_4cats_0_micro_macro.csv', sep = ''))
FCN <- read_csv(paste(path, 'Seawater_4cats_1_micro_macro.csv', sep = ''))
LSTM_FCN <- read_csv(paste(path, 'Seawater_4cats_2_micro_macro.csv', sep = ''))
ALSTM_FCN <- read_csv(paste(path, 'Seawater_4cats_3_micro_macro.csv', sep = ''))
combined1 <- bind_rows(LDA=LDA, 
                      LSTM=LSTM,
                      FCN=FCN,
                      `LSTM-FCN`=LSTM_FCN,
                      `ALSTM-FCN`=ALSTM_FCN,
                      .id = 'model')
```

```{r, fig.height=4, fig.width=6}
combined1 %>% 
  mutate(
    model = factor(model, levels = c('LDA', 'LSTM', 'FCN', 'LSTM-FCN', 'ALSTM-FCN'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 16) + 
  geom_line(aes(fpr_micro, tpr_micro, color = model), size = 1.5) +
  scale_x_continuous(limits = c(0, 1)) +
  scale_y_continuous(limits = c(0, 1)) +
  geom_abline(intercept = 0, slope = 1, color = 'black', linetype = 'dashed', size = 0.5) + 
  labs(x = 'False Positive Rate', y = 'True Positive Rate', color = '') +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial"))
```





## Faceted micro

```{r}
combined2 <- bind_rows(`11 classes`=combined, 
                      `4 classes`=combined1,
                      .id = 'dataset_label')
```

```{r, fig.height=4, fig.width=8}
combined2 %>% 
  mutate(
    model = factor(model, levels = c('LDA', 'LSTM', 'FCN', 'LSTM-FCN', 'ALSTM-FCN')),
    dataset_label = factor(dataset_label, levels = c('4 classes', '11 classes'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 18) + 
  geom_line(aes(fpr_micro, tpr_micro, color = model), size = 1.5) +
  facet_grid(.~dataset_label, scales = 'free') +
  scale_x_continuous(limits = c(0, 1)) +
  scale_y_continuous(limits = c(0, 1)) +
  geom_abline(intercept = 0, slope = 1, color = 'black', linetype = 'dashed', size = 0.5) + 
  labs(x = 'False Positive Rate', y = 'True Positive Rate', color = '') +
  theme(axis.text = element_text(size=12, color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(strip.text.x = element_text(size=18, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  theme(strip.text.x = element_text(color = "black", family="Arial"), 
        strip.background = element_blank())
```

## Faceted macro


```{r, fig.height=4, fig.width=8}
combined2 %>% 
  mutate(
    model = factor(model, levels = c('LDA', 'LSTM', 'FCN', 'LSTM-FCN', 'ALSTM-FCN')),
    dataset_label = factor(dataset_label, levels = c('4 classes', '11 classes'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 16) + 
  geom_line(aes(fpr_macro, tpr_macro, color = model), size = 1.5) +
  facet_grid(.~dataset_label, scales = 'free') +
  scale_x_continuous(limits = c(0, 1)) +
  scale_y_continuous(limits = c(0, 1)) +
  geom_abline(intercept = 0, slope = 1, color = 'black', linetype = 'dashed', size = 0.5) + 
  labs(x = 'False Positive Rate', y = 'True Positive Rate', color = '') +
  theme(axis.text = element_text(size=12, color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(strip.text.y = element_text(color = "black", family="Arial"), 
        strip.background = element_blank()) +
  theme(strip.text.x = element_text(color = "black", family="Arial"), 
        strip.background = element_blank())
```

































# 111718 including Explosives and Explosives_3cats this time

(No gen)
-- Constants and lists
epochs=500
seconds=120
array=("Seawater" "Seawater_4cats" "Explosives" "Explosives_3cats")
array2=(8 9 10 11) dataset_index
array3=(128 0 128 128) LCN
array4=(0.2 0.2 0.5 0.2) Training/test split
array5=(8 8 128 128) batch size


```{r}
path <- '~/results/no_gen_four_datasets_111718/Seawater/ROCAUC/'

rocauc1 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)

replacement_vec <- c("0"="LSTM", "1"="FCN", "2"="LSTM-FCN", "3"="ALSTM-FCN")
rocauc1$model <- str_replace_all(rocauc1$model, replacement_vec)
rocauc1
```

```{r}
path <- '~/results/no_gen_four_datasets_111718/Seawater_4cats/ROCAUC/'

rocauc2 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)

replacement_vec <- c("0"="LSTM", "1"="FCN", "2"="LSTM-FCN", "3"="ALSTM-FCN")
rocauc2$model <- str_replace_all(rocauc2$model, replacement_vec)
rocauc2
```


```{r}
path <- '~/results/no_gen_four_datasets_111718/Explosives/ROCAUC/'

rocauc3 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)

replacement_vec <- c("0"="LSTM", "1"="FCN", "2"="LSTM-FCN", "3"="ALSTM-FCN")
rocauc3$model <- str_replace_all(rocauc3$model, replacement_vec)
rocauc3
```

```{r}
path <- '~/results/no_gen_four_datasets_111718/Explosives_3cats/ROCAUC/'

rocauc4 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)

replacement_vec <- c("0"="LSTM", "1"="FCN", "2"="LSTM-FCN", "3"="ALSTM-FCN")
rocauc4$model <- str_replace_all(rocauc4$model, replacement_vec)
rocauc4
```




```{r}
combined <- bind_rows(Seawater_11 = rocauc1, 
                      Seawater_4 = rocauc2, 
                      Explosives_11 = rocauc3,
                      Explosives_3 = rocauc4,
                      .id = 'dataset_label')
combined$dataset_label <- str_replace_all(combined$dataset_label, "Seawater_11", "Seawater (11 classes)")
combined$dataset_label <- str_replace_all(combined$dataset_label, "Seawater_4", "Seawater (4 classes)")
combined$dataset_label <- str_replace_all(combined$dataset_label, "Explosives_11", "Explosives (11 classes)")
combined$dataset_label <- str_replace_all(combined$dataset_label, "Explosives_3", "Explosives (3 classes)")
```



```{r}
combined
```


## Micro

```{r, fig.height=9, fig.width=4}
combined %>% 
  # select(model, micro, macro, dataset_label) %>% 
  select(model, micro, dataset_label) %>% 
  gather(k, v, -model, -dataset_label) %>% 
  mutate(
    model = factor(model, levels = c('LDA', 'LSTM', 'FCN', 'LSTM-FCN', 'ALSTM-FCN')),
    dataset_label = factor(dataset_label, levels = c('Seawater (4 classes)', 
                                                     'Seawater (11 classes)',
                                                     'Explosives (3 classes)',
                                                     'Explosives (11 classes)')
                           )
  ) %>% 
  ggplot() +
  theme_bw(base_size = 18) +
  geom_boxplot(aes(model, v, fill = model)) +
  facet_grid(dataset_label~., scales = 'free_y') +
  # facet_grid(dataset_label~k, scales = 'free') +
  guides(fill=FALSE) +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(strip.text.y = element_text(size=12, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  # scale_y_continuous(limits = c(0.85, 1.0)) +
  labs(x = 'Model', y = 'micro-average AUC') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


## Macro

```{r, fig.height=4, fig.width=10}
combined %>% 
  # select(model, micro, macro, dataset_label) %>% 
  select(model, macro, dataset_label) %>% 
  gather(k, v, -model, -dataset_label) %>% 
  mutate(
    model = factor(model, levels = c('LDA', 'LSTM', 'FCN', 'LSTM-FCN', 'ALSTM-FCN')),
    dataset_label = factor(dataset_label, levels = c('Seawater (4 classes)', 
                                                     'Seawater (11 classes)',
                                                     'Explosives (3 classes)',
                                                     'Explosives (11 classes)')
                           )
  ) %>% 
  ggplot() +
  theme_bw(base_size = 18) +
  geom_boxplot(aes(model, v, fill = model)) +
  facet_grid(.~dataset_label, scales = 'free') +
  # facet_grid(dataset_label~k, scales = 'free') +
  guides(fill=FALSE) +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(strip.text.x = element_text(size=14, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  # scale_y_continuous(limits = c(0.6, 1.0)) +
  labs(x = 'Model', y = 'macro-average AUC') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```






# 111618 no_gen plotting ROC curves


```{r}
path <- '~/results/no_gen_four_datasets_111718/Seawater/rep_ROC/'

LDA <- read_csv(paste(path, 'Seawater_LDA_micro_macro.csv', sep = ''))
LSTM <- read_csv(paste(path, 'Seawater_0_micro_macro.csv', sep = ''))
FCN <- read_csv(paste(path, 'Seawater_1_micro_macro.csv', sep = ''))
LSTM_FCN <- read_csv(paste(path, 'Seawater_2_micro_macro.csv', sep = ''))
ALSTM_FCN <- read_csv(paste(path, 'Seawater_3_micro_macro.csv', sep = ''))
combined <- bind_rows(LDA=LDA, 
                      LSTM=LSTM,
                      FCN=FCN,
                      `LSTM-FCN`=LSTM_FCN,
                      `ALSTM-FCN`=ALSTM_FCN,
                      .id = 'model')
```



```{r}
combined
```


```{r, fig.height=4, fig.width=6}
combined %>% 
  mutate(
    model = factor(model, levels = c('LDA', 'LSTM', 'FCN', 'LSTM-FCN', 'ALSTM-FCN'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 16) + 
  geom_line(aes(fpr_micro, tpr_micro, color = model), size = 1.5) +
  scale_x_continuous(limits = c(0, 1)) +
  scale_y_continuous(limits = c(0, 1)) +
  geom_abline(intercept = 0, slope = 1, color = 'black', linetype = 'dashed', size = 0.5) + 
  labs(x = 'False Positive Rate', y = 'True Positive Rate', color = '') +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial"))
```




```{r}
path <- '~/results/no_gen_four_datasets_111718/Seawater_4cats/rep_ROC/'


LDA <- read_csv(paste(path, 'Seawater_4cats_LDA_micro_macro.csv', sep = ''))
LSTM <- read_csv(paste(path, 'Seawater_4cats_0_micro_macro.csv', sep = ''))
FCN <- read_csv(paste(path, 'Seawater_4cats_1_micro_macro.csv', sep = ''))
LSTM_FCN <- read_csv(paste(path, 'Seawater_4cats_2_micro_macro.csv', sep = ''))
ALSTM_FCN <- read_csv(paste(path, 'Seawater_4cats_3_micro_macro.csv', sep = ''))
combined1 <- bind_rows(LDA=LDA, 
                      LSTM=LSTM,
                      FCN=FCN,
                      `LSTM-FCN`=LSTM_FCN,
                      `ALSTM-FCN`=ALSTM_FCN,
                      .id = 'model')
```

```{r, fig.height=4, fig.width=6}
combined1 %>% 
  mutate(
    model = factor(model, levels = c('LDA', 'LSTM', 'FCN', 'LSTM-FCN', 'ALSTM-FCN'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 16) + 
  geom_line(aes(fpr_micro, tpr_micro, color = model), size = 1.5) +
  scale_x_continuous(limits = c(0, 1)) +
  scale_y_continuous(limits = c(0, 1)) +
  geom_abline(intercept = 0, slope = 1, color = 'black', linetype = 'dashed', size = 0.5) + 
  labs(x = 'False Positive Rate', y = 'True Positive Rate', color = '') +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial"))
```





```{r}
path <- '~/results/no_gen_four_datasets_111718/Explosives/rep_ROC/'

LDA <- read_csv(paste(path, 'Explosives_LDA_micro_macro.csv', sep = ''))
LSTM <- read_csv(paste(path, 'Explosives_0_micro_macro.csv', sep = ''))
FCN <- read_csv(paste(path, 'Explosives_1_micro_macro.csv', sep = ''))
LSTM_FCN <- read_csv(paste(path, 'Explosives_2_micro_macro.csv', sep = ''))
ALSTM_FCN <- read_csv(paste(path, 'Explosives_3_micro_macro.csv', sep = ''))
combined2 <- bind_rows(LDA=LDA, 
                      LSTM=LSTM,
                      FCN=FCN,
                      `LSTM-FCN`=LSTM_FCN,
                      `ALSTM-FCN`=ALSTM_FCN,
                      .id = 'model')
```

```{r, fig.height=4, fig.width=6}
combined2 %>% 
  mutate(
    model = factor(model, levels = c('LDA', 'LSTM', 'FCN', 'LSTM-FCN', 'ALSTM-FCN'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 16) + 
  geom_line(aes(fpr_micro, tpr_micro, color = model), size = 1.5) +
  scale_x_continuous(limits = c(0, 1)) +
  scale_y_continuous(limits = c(0, 1)) +
  geom_abline(intercept = 0, slope = 1, color = 'black', linetype = 'dashed', size = 0.5) + 
  labs(x = 'False Positive Rate', y = 'True Positive Rate', color = '') +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial"))
```



```{r}
path <- '~/results/no_gen_four_datasets_111718/Explosives_3cats/rep_ROC/'

LDA <- read_csv(paste(path, 'Explosives_3cats_LDA_micro_macro.csv', sep = ''))
LSTM <- read_csv(paste(path, 'Explosives_3cats_0_micro_macro.csv', sep = ''))
FCN <- read_csv(paste(path, 'Explosives_3cats_1_micro_macro.csv', sep = ''))
LSTM_FCN <- read_csv(paste(path, 'Explosives_3cats_2_micro_macro.csv', sep = ''))
ALSTM_FCN <- read_csv(paste(path, 'Explosives_3cats_3_micro_macro.csv', sep = ''))
combined3 <- bind_rows(LDA=LDA, 
                      LSTM=LSTM,
                      FCN=FCN,
                      `LSTM-FCN`=LSTM_FCN,
                      `ALSTM-FCN`=ALSTM_FCN,
                      .id = 'model')
```

```{r, fig.height=4, fig.width=6}
combined3 %>% 
  mutate(
    model = factor(model, levels = c('LDA', 'LSTM', 'FCN', 'LSTM-FCN', 'ALSTM-FCN'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 16) + 
  geom_line(aes(fpr_micro, tpr_micro, color = model), size = 1.5) +
  scale_x_continuous(limits = c(0, 1)) +
  scale_y_continuous(limits = c(0, 1)) +
  geom_abline(intercept = 0, slope = 1, color = 'black', linetype = 'dashed', size = 0.5) + 
  labs(x = 'False Positive Rate', y = 'True Positive Rate', color = '') +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial"))
```










## Faceted micro

```{r}
combined4 <- bind_rows(`Seawater (11 classes)` = combined, 
                      `Seawater (4 classes)` = combined1,
                      `Explosives (11 classes)` = combined2,
                      `Explosives (3 classes)` = combined3,
                      .id = 'dataset_label')
```

```{r, fig.height=9, fig.width=5}
combined4 %>% 
  mutate(
    model = factor(model, levels = c('LDA', 'LSTM', 'FCN', 'LSTM-FCN', 'ALSTM-FCN')),
    dataset_label = factor(dataset_label, levels = c('Seawater (4 classes)', 
                                                     'Seawater (11 classes)',
                                                     'Explosives (3 classes)',
                                                     'Explosives (11 classes)')
                           )
  ) %>% 
  ggplot() +
  theme_bw(base_size = 18) + 
  geom_line(aes(fpr_micro, tpr_micro, color = model), size = 1.5) +
  facet_grid(dataset_label~., scales = 'free') +
  scale_x_continuous(limits = c(0, 1)) +
  scale_y_continuous(limits = c(0, 1)) +
  geom_abline(intercept = 0, slope = 1, color = 'black', linetype = 'dashed', size = 0.5) + 
  labs(x = 'False Positive Rate', y = 'True Positive Rate', color = '') +
  theme(axis.text = element_text(size=12, color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(strip.text.y = element_text(size=12, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  theme(strip.text.x = element_text(color = "black", family="Arial"), 
        strip.background = element_blank())
```

## Faceted macro


```{r, fig.height=3.5, fig.width=12}
combined4 %>% 
  mutate(
    model = factor(model, levels = c('LDA', 'LSTM', 'FCN', 'LSTM-FCN', 'ALSTM-FCN')),
    dataset_label = factor(dataset_label, levels = c('Seawater (4 classes)', 
                                                     'Seawater (11 classes)',
                                                     'Explosives (3 classes)',
                                                     'Explosives (11 classes)')
                           )
  ) %>% 
  ggplot() +
  theme_bw(base_size = 16) + 
  geom_line(aes(fpr_macro, tpr_macro, color = model), size = 1.5) +
  facet_grid(.~dataset_label, scales = 'free') +
  scale_x_continuous(limits = c(0, 1)) +
  scale_y_continuous(limits = c(0, 1)) +
  geom_abline(intercept = 0, slope = 1, color = 'black', linetype = 'dashed', size = 0.5) + 
  labs(x = 'False Positive Rate', y = 'True Positive Rate', color = '') +
  theme(axis.text = element_text(size=12, color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(strip.text.y = element_text(color = "black", family="Arial"), 
        strip.background = element_blank()) +
  theme(strip.text.x = element_text(color = "black", family="Arial"), 
        strip.background = element_blank())
```











# Optimizing LCN for ALSTM-FCN for each dataset

Constant: model = 3; batch size = 32.

Looped over 128 64 32 16 8 4 LCN


```{r}
path <- '~/results/ALSTM_FCN_LCN_optimization_111818/Seawater/ROCAUC/'

rocauc1 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)
rocauc1
```

```{r}
path <- '~/results/ALSTM_FCN_LCN_optimization_111818/Seawater_4cats/ROCAUC/'

rocauc2 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  # bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)

rocauc2
```

```{r}
path <- '~/results/ALSTM_FCN_LCN_optimization_111818/Explosives/ROCAUC/'  # path <- '~/results/Seawater_150epochs/ROCAUC/'

rocauc3 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)
rocauc3
```

```{r}
path <- '~/results/ALSTM_FCN_LCN_optimization_111818/Explosives_3cats/ROCAUC/'

rocauc4 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)

rocauc4
```



```{r}
combined <- bind_rows(Seawater_11 = rocauc1, 
                      Seawater_4 = rocauc2, 
                      Explosives_11 = rocauc3,
                      Explosives_3 = rocauc4,
                      .id = 'dataset_label')
combined$dataset_label <- str_replace_all(combined$dataset_label, "Seawater_11", "Seawater (11 classes)")
combined$dataset_label <- str_replace_all(combined$dataset_label, "Seawater_4", "Seawater (4 classes)")
combined$dataset_label <- str_replace_all(combined$dataset_label, "Explosives_11", "Explosives (11 classes)")
combined$dataset_label <- str_replace_all(combined$dataset_label, "Explosives_3", "Explosives (3 classes)")
```

```{r}
combined
```



```{r}
combined$lcn <- rep(c(128, 64, 32, 16, 8, 4), 11)
```


```{r}
combined %>% 
  filter(model == 3) %>% 
  select(lcn, micro, macro, dataset_label) %>% 
  gather(k, v, -lcn, -dataset_label) %>% 
  mutate(
    lcn = factor(lcn, levels = c(4, 8, 16, 32, 64, 128)),
    dataset_label = factor(dataset_label, levels = c('Seawater (4 classes)', 
                                                     'Seawater (11 classes)',
                                                     'Explosives (3 classes)',
                                                     'Explosives (11 classes)')
                           )
  ) 
```


```{r, fig.width=10}
combined %>% 
  filter(model == 3) %>% 
  select(lcn, micro, macro, dataset_label) %>% 
  gather(k, v, -lcn, -dataset_label) %>% 
  mutate(
    lcn = factor(lcn, levels = c(4, 8, 16, 32, 64, 128)),
    dataset_label = factor(dataset_label, levels = c('Seawater (4 classes)', 
                                                     'Seawater (11 classes)',
                                                     'Explosives (3 classes)',
                                                     'Explosives (11 classes)')
                           ),
    k = factor(k, levels = c('micro', 'macro'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 18) +
  geom_boxplot(aes(lcn, v, fill = dataset_label)) +
  # facet_grid(.~k, scales = 'free') +
  facet_grid(k~dataset_label, scales = 'free') +
  guides(fill=FALSE) +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(plot.title = element_text(size=16, color = "black", family="Arial")) +
  theme(strip.text.y = element_text(size=18, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  theme(strip.text.x = element_text(size=12, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  # scale_y_continuous(limits = c(0.25, 1)) +
  labs(x = 'LSTM cell number', y = 'average AUC', title = 'ALSTM-FCN, 500 epochs, LCN optimization')

  # ggsave('test.png')
```

Looks like if the LCN for ALSTM-FCN is set to 32, you'll do okay.

Maybe relabel micro and macro --> micro-average and macro-average. And average AUC --> AUC.







# Optimizing batch size for ALSTM-FCN for each dataset

Constant: model = 3; LCN = 32.

Looped over 128 64 32 16 8 4 batch sizes



```{r}
path <- '~/results/ALSTM_FCN_batchsize_optimization_111918/Seawater/ROCAUC/'  # path <- '~/results/Seawater_150epochs/ROCAUC/'

rocauc1 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)
rocauc1
```


```{r}
path <- '~/results/ALSTM_FCN_batchsize_optimization_111918/Seawater_4cats/ROCAUC/'

rocauc2 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)

rocauc2
```

```{r}
path <- '~/results/ALSTM_FCN_batchsize_optimization_111918/Explosives/ROCAUC/'  # path <- '~/results/Seawater_150epochs/ROCAUC/'

rocauc3 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)
rocauc3
```


```{r}
path <- '~/results/ALSTM_FCN_batchsize_optimization_111918/Explosives_3cats/ROCAUC/'

rocauc4 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)

rocauc4
```



```{r}
combined <- bind_rows(Seawater_11 = rocauc1, 
                      Seawater_4 = rocauc2, 
                      Explosives_11 = rocauc3,
                      Explosives_3 = rocauc4,
                      .id = 'dataset_label')
combined$dataset_label <- str_replace_all(combined$dataset_label, "Seawater_11", "Seawater (11 classes)")
combined$dataset_label <- str_replace_all(combined$dataset_label, "Seawater_4", "Seawater (4 classes)")
combined$dataset_label <- str_replace_all(combined$dataset_label, "Explosives_11", "Explosives (11 classes)")
combined$dataset_label <- str_replace_all(combined$dataset_label, "Explosives_3", "Explosives (3 classes)")
```

```{r}
combined
```


```{r}
combined$batchsize <- rep(c(128, 64, 32, 16, 8, 4), 12)
```



```{r, fig.width=10}
combined %>% 
  filter(model == 3) %>% 
  select(batchsize, micro, macro, dataset_label) %>% 
  gather(k, v, -batchsize, -dataset_label) %>% 
  mutate(
    batchsize = factor(batchsize, levels = c(4, 8, 16, 32, 64, 128)),
    dataset_label = factor(dataset_label, levels = c('Seawater (4 classes)', 
                                                     'Seawater (11 classes)',
                                                     'Explosives (3 classes)',
                                                     'Explosives (11 classes)')
                           ),
    k = factor(k, levels = c('micro', 'macro'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 18) +
  geom_boxplot(aes(batchsize, v, fill = dataset_label)) +
  facet_grid(k~dataset_label, scales = 'free') +
  guides(fill=FALSE) +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(plot.title = element_text(size=16, color = "black", family="Arial")) +
  theme(strip.text.y = element_text(size=18, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  theme(strip.text.x = element_text(size=12, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  # scale_y_continuous(limits = c(0.85, 0.96)) +
  labs(x = 'batch size', y = 'average AUC', title = 'ALSTM-FCN, 500 epochs, batch size optimization')
```


























# Optimizing LCN for LSTM-FCN for each dataset

Constant: model = 2; batch size = 32.

Looped over 128 64 32 16 8 4 LCN


```{r}
path <- '~/results/LSTM_FCN_LCN_optimization_111918/Seawater/ROCAUC/'  # path <- '~/results/Seawater_150epochs/ROCAUC/'

rocauc1 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)
rocauc1
```

```{r}
path <- '~/results/LSTM_FCN_LCN_optimization_111918/Seawater_4cats/ROCAUC/'

rocauc2 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)

rocauc2
```

```{r}
path <- '~/results/LSTM_FCN_LCN_optimization_111918/Explosives/ROCAUC/'  # path <- '~/results/Seawater_150epochs/ROCAUC/'

rocauc3 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)
rocauc3
```

```{r}
path <- '~/results/LSTM_FCN_LCN_optimization_111918/Explosives_3cats/ROCAUC/'

rocauc4 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)

rocauc4
```



```{r}
combined <- bind_rows(Seawater_11 = rocauc1, 
                      Seawater_4 = rocauc2, 
                      Explosives_11 = rocauc3,
                      Explosives_3 = rocauc4,
                      .id = 'dataset_label')
combined$dataset_label <- str_replace_all(combined$dataset_label, "Seawater_11", "Seawater (11 classes)")
combined$dataset_label <- str_replace_all(combined$dataset_label, "Seawater_4", "Seawater (4 classes)")
combined$dataset_label <- str_replace_all(combined$dataset_label, "Explosives_11", "Explosives (11 classes)")
combined$dataset_label <- str_replace_all(combined$dataset_label, "Explosives_3", "Explosives (3 classes)")
```

```{r}
combined
```



```{r}
combined$lcn <- rep(c(128, 64, 32, 16, 8, 4), 12)
```


```{r}
combined %>% 
  filter(model == 2) %>% 
  select(lcn, micro, macro, dataset_label) %>% 
  gather(k, v, -lcn, -dataset_label) %>% 
  mutate(
    lcn = factor(lcn, levels = c(4, 8, 16, 32, 64, 128)),
    dataset_label = factor(dataset_label, levels = c('Seawater (4 classes)', 
                                                     'Seawater (11 classes)',
                                                     'Explosives (3 classes)',
                                                     'Explosives (11 classes)')
                           )
  ) 
```


```{r, fig.width=10}
combined %>% 
  filter(model == 2) %>% 
  select(lcn, micro, macro, dataset_label) %>% 
  gather(k, v, -lcn, -dataset_label) %>% 
  mutate(
    lcn = factor(lcn, levels = c(4, 8, 16, 32, 64, 128)),
    dataset_label = factor(dataset_label, levels = c('Seawater (4 classes)', 
                                                     'Seawater (11 classes)',
                                                     'Explosives (3 classes)',
                                                     'Explosives (11 classes)')
                           ),
    k = factor(k, levels = c('micro', 'macro'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 18) +
  geom_boxplot(aes(lcn, v, fill = dataset_label)) +
  # facet_grid(.~k, scales = 'free') +
  facet_grid(k~dataset_label, scales = 'free') +
  guides(fill=FALSE) +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(plot.title = element_text(size=16, color = "black", family="Arial")) +
  theme(strip.text.y = element_text(size=18, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  theme(strip.text.x = element_text(size=12, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  # scale_y_continuous(limits = c(0.25, 1)) +
  labs(x = 'LSTM cell number', y = 'average AUC', title = 'LSTM-FCN, 500 epochs, LCN optimization')

  # ggsave('test.png')
```


Since no real trend is seen, go with LCN = 32, like ALSTM-FCN.













# Optimizing batch size for LSTM-FCN for each dataset

Constant: model = 2; LCN = 32.

Looped over 128 64 32 16 8 4 batch sizes

```{r}
path <- '~/results/LSTM_FCN_batchsize_optimization_111918/Seawater/ROCAUC/'  # path <- '~/results/Seawater_150epochs/ROCAUC/'

rocauc1 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)
rocauc1
```


```{r}
path <- '~/results/LSTM_FCN_batchsize_optimization_111918/Seawater_4cats/ROCAUC/'

rocauc2 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)

rocauc2
```

```{r}
path <- '~/results/LSTM_FCN_batchsize_optimization_111918/Explosives/ROCAUC/'  # path <- '~/results/Seawater_150epochs/ROCAUC/'

rocauc3 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)
rocauc3
```


```{r}
path <- '~/results/LSTM_FCN_batchsize_optimization_111918/Explosives_3cats/ROCAUC/'

rocauc4 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)

rocauc4
```



```{r}
combined <- bind_rows(Seawater_11 = rocauc1, 
                      Seawater_4 = rocauc2, 
                      Explosives_11 = rocauc3,
                      Explosives_3 = rocauc4,
                      .id = 'dataset_label')
combined$dataset_label <- str_replace_all(combined$dataset_label, "Seawater_11", "Seawater (11 classes)")
combined$dataset_label <- str_replace_all(combined$dataset_label, "Seawater_4", "Seawater (4 classes)")
combined$dataset_label <- str_replace_all(combined$dataset_label, "Explosives_11", "Explosives (11 classes)")
combined$dataset_label <- str_replace_all(combined$dataset_label, "Explosives_3", "Explosives (3 classes)")
```

```{r}
combined
```


```{r}
combined$batchsize <- rep(c(128, 64, 32, 16, 8, 4), 12)
```



```{r, fig.width=10}
combined %>% 
  filter(model == 2) %>% 
  select(batchsize, micro, macro, dataset_label) %>% 
  gather(k, v, -batchsize, -dataset_label) %>% 
  mutate(
    batchsize = factor(batchsize, levels = c(4, 8, 16, 32, 64, 128)),
    dataset_label = factor(dataset_label, levels = c('Seawater (4 classes)', 
                                                     'Seawater (11 classes)',
                                                     'Explosives (3 classes)',
                                                     'Explosives (11 classes)')
                           ),
    k = factor(k, levels = c('micro', 'macro'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 18) +
  geom_boxplot(aes(batchsize, v, fill = dataset_label)) +
  facet_grid(k~dataset_label, scales = 'free') +
  guides(fill=FALSE) +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(plot.title = element_text(size=16, color = "black", family="Arial")) +
  theme(strip.text.y = element_text(size=18, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  theme(strip.text.x = element_text(size=12, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  # scale_y_continuous(limits = c(0.85, 0.96)) +
  labs(x = 'batch size', y = 'average AUC', title = 'LSTM-FCN, 500 epochs, batch size optimization')
```










# Optimizing batch size for FCN for each dataset

Constant: model = 1; LCN = none

Looped over 128 64 32 16 8 4 batch sizes


```{r}
path <- '~/results/FCN_batchsize_optimization_111918/Seawater/ROCAUC/'  # path <- '~/results/Seawater_150epochs/ROCAUC/'

rocauc1 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)
rocauc1
```


```{r}
path <- '~/results/FCN_batchsize_optimization_111918/Seawater_4cats/ROCAUC/'

rocauc2 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)

rocauc2
```

```{r}
path <- '~/results/FCN_batchsize_optimization_111918/Explosives/ROCAUC/'  # path <- '~/results/Seawater_150epochs/ROCAUC/'

rocauc3 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)
rocauc3
```


```{r}
path <- '~/results/FCN_batchsize_optimization_111918/Explosives_3cats/ROCAUC/'

rocauc4 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)

rocauc4
```



```{r}
combined <- bind_rows(Seawater_11 = rocauc1, 
                      Seawater_4 = rocauc2, 
                      Explosives_11 = rocauc3,
                      Explosives_3 = rocauc4,
                      .id = 'dataset_label')
combined$dataset_label <- str_replace_all(combined$dataset_label, "Seawater_11", "Seawater (11 classes)")
combined$dataset_label <- str_replace_all(combined$dataset_label, "Seawater_4", "Seawater (4 classes)")
combined$dataset_label <- str_replace_all(combined$dataset_label, "Explosives_11", "Explosives (11 classes)")
combined$dataset_label <- str_replace_all(combined$dataset_label, "Explosives_3", "Explosives (3 classes)")
```

```{r}
combined
```


```{r}
combined$batchsize <- rep(c(128, 64, 32, 16, 8, 4), 12)
```



```{r, fig.width=10}
combined %>% 
  filter(model == 1) %>% 
  select(batchsize, micro, macro, dataset_label) %>% 
  gather(k, v, -batchsize, -dataset_label) %>% 
  mutate(
    batchsize = factor(batchsize, levels = c(4, 8, 16, 32, 64, 128)),
    dataset_label = factor(dataset_label, levels = c('Seawater (4 classes)', 
                                                     'Seawater (11 classes)',
                                                     'Explosives (3 classes)',
                                                     'Explosives (11 classes)')
                           ),
    k = factor(k, levels = c('micro', 'macro'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 18) +
  geom_boxplot(aes(batchsize, v, fill = dataset_label)) +
  facet_grid(k~dataset_label, scales = 'free') +
  guides(fill=FALSE) +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(plot.title = element_text(size=16, color = "black", family="Arial")) +
  theme(strip.text.y = element_text(size=18, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  theme(strip.text.x = element_text(size=12, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  # scale_y_continuous(limits = c(0.85, 0.96)) +
  labs(x = 'batch size', y = 'average AUC', title = 'FCN, 500 epochs, batch size optimization')
```









# Optimizing LCN for LSTM for each dataset

Constant: model = 0; batch size = 32.

Looped over 128 64 32 16 8 4 LCNs

```{r, warning=FALSE, message=FALSE}
path <- '~/results/LSTM_LCN_optimization_112018/Seawater/ROCAUC/'  # path <- '~/results/Seawater_150epochs/ROCAUC/'

rocauc1 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)
```

```{r, warning=FALSE, message=FALSE}
path <- '~/results/LSTM_LCN_optimization_112018/Seawater_4cats/ROCAUC/'

rocauc2 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)
```

```{r, warning=FALSE, message=FALSE}
path <- '~/results/LSTM_LCN_optimization_112018/Explosives/ROCAUC/'  # path <- '~/results/Seawater_150epochs/ROCAUC/'

rocauc3 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)
```

```{r, warning=FALSE, message=FALSE}
path <- '~/results/LSTM_LCN_optimization_112018/Explosives_3cats/ROCAUC/'

rocauc4 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)
```



```{r}
combined <- bind_rows(Seawater_11 = rocauc1, 
                      Seawater_4 = rocauc2, 
                      Explosives_11 = rocauc3,
                      Explosives_3 = rocauc4,
                      .id = 'dataset_label')
combined$dataset_label <- str_replace_all(combined$dataset_label, "Seawater_11", "Seawater (11 classes)")
combined$dataset_label <- str_replace_all(combined$dataset_label, "Seawater_4", "Seawater (4 classes)")
combined$dataset_label <- str_replace_all(combined$dataset_label, "Explosives_11", "Explosives (11 classes)")
combined$dataset_label <- str_replace_all(combined$dataset_label, "Explosives_3", "Explosives (3 classes)")
```

```{r}
combined
```



```{r}
combined$lcn <- rep(c(128, 64, 32, 16, 8, 4), 12)
```


```{r}
combined %>% 
  filter(model == 0) %>% 
  select(lcn, micro, macro, dataset_label) %>% 
  gather(k, v, -lcn, -dataset_label) %>% 
  mutate(
    lcn = factor(lcn, levels = c(4, 8, 16, 32, 64, 128)),
    dataset_label = factor(dataset_label, levels = c('Seawater (4 classes)', 
                                                     'Seawater (11 classes)',
                                                     'Explosives (3 classes)',
                                                     'Explosives (11 classes)')
                           )
  ) 
```


```{r, fig.width=10}
combined %>% 
  filter(model == 0) %>% 
  select(lcn, micro, macro, dataset_label) %>% 
  gather(k, v, -lcn, -dataset_label) %>% 
  mutate(
    lcn = factor(lcn, levels = c(4, 8, 16, 32, 64, 128)),
    dataset_label = factor(dataset_label, levels = c('Seawater (4 classes)', 
                                                     'Seawater (11 classes)',
                                                     'Explosives (3 classes)',
                                                     'Explosives (11 classes)')
                           ),
    k = factor(k, levels = c('micro', 'macro'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 18) +
  geom_boxplot(aes(lcn, v, fill = dataset_label)) +
  # facet_grid(.~k, scales = 'free') +
  facet_grid(k~dataset_label, scales = 'free') +
  guides(fill=FALSE) +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(plot.title = element_text(size=16, color = "black", family="Arial")) +
  theme(strip.text.y = element_text(size=18, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  theme(strip.text.x = element_text(size=12, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  # scale_y_continuous(limits = c(0.25, 1)) +
  labs(x = 'LSTM cell number', y = 'average AUC', title = 'LSTM, 500 epochs, LCN optimization')

  ggsave('test_lcn.png')
```






# Optimizing batch size for LSTM for each dataset

Constant: model = 0; LCN = 128.

Looped over 128 64 32 16 8 4 batch sizes


```{r, warning=FALSE, message=FALSE}
path <- '~/results/LSTM_batchsize_optimization_112018/Seawater/ROCAUC/'  # path <- '~/results/Seawater_150epochs/ROCAUC/'

rocauc1 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)
```


```{r, warning=FALSE, message=FALSE}
path <- '~/results/LSTM_batchsize_optimization_112018/Seawater_4cats/ROCAUC/'

rocauc2 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)
```

```{r, warning=FALSE, message=FALSE}
path <- '~/results/LSTM_batchsize_optimization_112018/Explosives/ROCAUC/'  # path <- '~/results/Seawater_150epochs/ROCAUC/'

rocauc3 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)
```


```{r, warning=FALSE, message=FALSE}
path <- '~/results/LSTM_batchsize_optimization_112018/Explosives_3cats/ROCAUC/'

rocauc4 <- read_csv(paste(path, 'ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>% 
  bind_rows(., read_csv(paste(path, 'ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
  na.omit() %>% 
  rename('dataset' = X1,
         'model' = X2,
         'micro' = X3,
         'macro' = X4)
```



```{r}
combined <- bind_rows(Seawater_11 = rocauc1, 
                      Seawater_4 = rocauc2, 
                      Explosives_11 = rocauc3,
                      Explosives_3 = rocauc4,
                      .id = 'dataset_label')
combined$dataset_label <- str_replace_all(combined$dataset_label, "Seawater_11", "Seawater (11 classes)")
combined$dataset_label <- str_replace_all(combined$dataset_label, "Seawater_4", "Seawater (4 classes)")
combined$dataset_label <- str_replace_all(combined$dataset_label, "Explosives_11", "Explosives (11 classes)")
combined$dataset_label <- str_replace_all(combined$dataset_label, "Explosives_3", "Explosives (3 classes)")
```

```{r}
combined
```


```{r}
combined$batchsize <- rep(c(128, 64, 32, 16, 8, 4), 12)
```



```{r, fig.width=10}
combined %>% 
  filter(model == 0) %>% 
  select(batchsize, micro, macro, dataset_label) %>% 
  gather(k, v, -batchsize, -dataset_label) %>% 
  mutate(
    batchsize = factor(batchsize, levels = c(4, 8, 16, 32, 64, 128)),
    dataset_label = factor(dataset_label, levels = c('Seawater (4 classes)', 
                                                     'Seawater (11 classes)',
                                                     'Explosives (3 classes)',
                                                     'Explosives (11 classes)')
                           ),
    k = factor(k, levels = c('micro', 'macro'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 18) +
  geom_boxplot(aes(batchsize, v, fill = dataset_label)) +
  facet_grid(k~dataset_label, scales = 'free') +
  guides(fill=FALSE) +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(plot.title = element_text(size=16, color = "black", family="Arial")) +
  theme(strip.text.y = element_text(size=18, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  theme(strip.text.x = element_text(size=12, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  # scale_y_continuous(limits = c(0.85, 0.96)) +
  labs(x = 'batch size', y = 'average AUC', title = 'LSTM, 500 epochs, batch size optimization')

ggsave('test_bs.png')
```




























# Plotting function

```{r, warning=FALSE, message=FALSE}

read_rocauc <- function(base_path, dataset_name){
  rocauc_out <- read_csv(paste(base_path, dataset_name, '/ROCAUC/ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
    bind_rows(., read_csv(paste(base_path, dataset_name, '/ROCAUC/ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>%
    bind_rows(., read_csv(paste(base_path, dataset_name, '/ROCAUC/ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
    na.omit() %>% 
    rename('dataset' = X1,
           'model' = X2,
           'micro' = X3,
           'macro' = X4)
  return(rocauc_out)
}

p <- '~/results/LSTM_FCN_LCN_optimization_111918/'
nums <- c(128, 64, 32, 16, 8, 4)

combined <- bind_rows(`Seawater (11 classes)` = read_rocauc(p, 'Seawater'), 
                      `Seawater (4 classes)` = read_rocauc(p, 'Seawater_4cats'), 
                      `Explosives (11 classes)` = read_rocauc(p, 'Explosives'), 
                      `Explosives (3 classes)` = read_rocauc(p, 'Explosives_3cats'), 
                      .id = 'dataset_label')

combined$lcn <- rep(nums, 12)
```



```{r, fig.width=10}
combined %>% 
  filter(model == 2) %>% 
  select(lcn, micro, macro, dataset_label) %>% 
  gather(k, v, -lcn, -dataset_label) %>% 
  mutate(
    lcn = factor(lcn, levels = rev(nums)),
    dataset_label = factor(dataset_label, levels = c('Seawater (4 classes)', 
                                                     'Seawater (11 classes)',
                                                     'Explosives (3 classes)',
                                                     'Explosives (11 classes)')),
    k = factor(k, levels = c('micro', 'macro'))
  ) %>% 
  ggplot() +
  theme_bw(base_size = 18) +
  geom_boxplot(aes(lcn, v, fill = dataset_label)) +
  facet_grid(k~dataset_label, scales = 'free') +
  guides(fill=FALSE) +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(plot.title = element_text(size=16, color = "black", family="Arial")) +
  theme(strip.text.y = element_text(size=18, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  theme(strip.text.x = element_text(size=12, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  labs(x = 'LSTM cell number', y = 'average AUC', title = 'LSTM-FCN, 500 epochs, LCN optimization')
```








# 112018 ROCAUC boxplots 


```{r, warning=FALSE, message=FALSE}

read_rocauc <- function(base_path, dataset_name){
  rocauc_out <- read_csv(paste(base_path, dataset_name, '/ROCAUC/ROCAUCs_1.csv', sep = ''), col_names = FALSE) %>% 
    bind_rows(., read_csv(paste(base_path, dataset_name, '/ROCAUC/ROCAUCs_2.csv', sep = ''), col_names = FALSE)) %>%
    bind_rows(., read_csv(paste(base_path, dataset_name, '/ROCAUC/ROCAUCs_3.csv', sep = ''), col_names = FALSE)) %>% 
    na.omit() %>% 
    rename('dataset' = X1,
           'model' = X2,
           'micro' = X3,
           'macro' = X4)
  return(rocauc_out)
}

p <- '~/results/rocauc_boxplot_112018/'

combined <- bind_rows(`Seawater (11 classes)` = read_rocauc(p, 'Seawater'), 
                      `Seawater (4 classes)` = read_rocauc(p, 'Seawater_4cats'), 
                      `Explosives (11 classes)` = read_rocauc(p, 'Explosives'), 
                      `Explosives (3 classes)` = read_rocauc(p, 'Explosives_3cats'), 
                      .id = 'dataset_label')
```



```{r}
combined
```

```{r}
replacement_vec <- c("0"="LSTM", "1"="FCN", "2"="LSTM-FCN", "3"="ALSTM-FCN")
combined$model <- str_replace_all(combined$model, replacement_vec)
```


```{r, fig.height=9, fig.width=4}
combined %>% 
  # select(model, micro, macro, dataset_label) %>% 
  select(model, micro, dataset_label) %>% 
  gather(k, v, -model, -dataset_label) %>% 
  mutate(
    model = factor(model, levels = c('LDA', 'LSTM', 'FCN', 'LSTM-FCN', 'ALSTM-FCN')),
    dataset_label = factor(dataset_label, levels = c('Seawater (4 classes)', 
                                                     'Seawater (11 classes)',
                                                     'Explosives (3 classes)',
                                                     'Explosives (11 classes)')
                           )
  ) %>% 
  ggplot() +
  theme_bw(base_size = 18) +
  geom_boxplot(aes(model, v, fill = model)) +
  facet_grid(dataset_label~., scales = 'free_y') +
  # facet_grid(dataset_label~k, scales = 'free') +
  guides(fill=FALSE) +
  theme(axis.text = element_text(color = "black", family="Arial")) +
  theme(axis.title = element_text(color = "black", family="Arial")) +
  theme(strip.text.y = element_text(size=12, color = "black", family="Arial"), 
        strip.background = element_blank()) +
  scale_y_continuous(limits = c(0.7, 1.0)) +
  labs(x = 'Model', y = 'micro-average AUC') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```







